---
title: "Exploratory PADLD Analyses"
author: "Ashlie"
date: "2024-09-19"
output: html_document
---
Exploratory Analyses: 
- does the CELF predict priming effects when collapsed across groups? YES for words, YES for pictures
- does the CELF predict priming effects in only TD kids? NO for words, YES for pictures
- does the TILLS predict priming effects when collapsed across groups? NO for words, NO for pictures
- does the TILLS predict priming effects in only TD kids? NO for words, NO for pictures
- does the magnitude of priming effects differ across ISIs when collapsed across groups? YES for words, NO for pictures
- does the magnitude of priming effects differ across ISIs in only TD kids? YES for words, NO for pictures
- do kids with DLD and age- and TONI-matched TD kids show different patterns of priming effects at the group level (i.e., original RQ 1 & 2 with balanced sample)? 
     MASKED WORDS
      DLD    TL
67     -     +
317    +     -  

     MASKED PICS
      DLD    TL
67     +     -
317    -     +  


- do TILLS scores of kids with DLD and age- and TONI-matched TD kids predict differences in priming effects at each ISI (i.e., original RQ 3 with balanced sample)? not sure yet--seems the values I used in my initial analyses might be wrong... 

```{r setup}

# Libraries
pacman::p_load(knitr, # rendering of .Rmd file
               lme4, # model specification/estimation
               afex, # anova and deriving p-values via LRTs from lmer
               broom.mixed, # extracting data from model fits
               faux, # generate correlated values
               tidyverse, # data wrangling and visualization 
               ggridges, # visualization
               viridis, # color schemes for visualization
               kableExtra, # helps with knitting the .Rmd file
               cowplot, # visualization tool to include multiple plots
               ggrain, # visualization tool for raincloud plots
               dplyr, # data manipulation tools
               here, # controlling directories/reproducibility
               tidyr, # formatting package
               readr, # data importation
               Hmisc, # visualization
               emmeans, # estimation of marginal means and contrasts
               sjstats, # estimation of marginal means and contrasts
               lmerTest, # deriving p-values from lmer
               MuMIn, # ?
               sjPlot, # APA formatting of numerical output
               car, # data wrangling and visualization,
               magrittr, # to use %>%
               ggpubr, # ? (Rose had it in her script)
               broom, # ? (Rose had it in her script)
               Matrix, # model specification/estimation,
               multcomp, # multiple comparison adjustments
               forcats, # organizing visualizations
               gtools, # data manipulation/wrangling
               fuzzySim, # FDR correction,
               ez, # anova
               apaTables, # visualization of anova output
               #renv # package versioning/reproducibility
               )

# Global theme set
set.seed(1234) # set random seed for reproducibility

knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)

#theme_set(theme_bw(base_size = 13) + theme(text = element_text(size=13), 
                             #axis.title=element_text(size=12),
                             #strip.text = element_text(margin=margin(2,0,2,0)), 
                             #panel.grid = element_blank()))

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE, fig.width=10, fig.height=8, fig.fullwidth=TRUE)

plot_theme <- 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18), 
        axis.text.x = element_text(size = 13), 
        axis.title.x = element_text(size = 13), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 13),
        strip.background = element_rect(color="white", fill="white", linewidth = 1.5, linetype="solid"))

options(scipen=999)
```

# Many N400 Channels Data (to examine priming x ISI x group effects at each prime visibility)
## Data Manipulations
```{r}
# Data from many electrodes to measure N400 more comprehensively
# Load data
manyn400chans_data <- read.csv(here("PADLD Data", "Analysis Data","All PADLD Critical Target Mean Amps (50ms pre post bl many electrodes).csv"),stringsAsFactors=TRUE) # mean amplitudes from 30 electrodes at 300 to 500ms post-target onset for all critical targets (with a +/- 50 ms baseline)

# Format data
manyn400chans_data %<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Participant.ID = factor(Participant.ID),
         Channel = factor(Channel),
         Priming=factor(Priming, levels=c("unprimed","primed")),
         ISI = factor(ISI,levels=c("67","317")),
         Experimental.Condition = factor(Experimental.Condition),
         Stimulus.Type = factor(Stimulus.Type),
         Prime.Visibility = factor (Prime.Visibility),
         Trial.Type = factor(Trial.Type),
         Group = factor(Group,levels=c("TL","DLD")),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.c = as.numeric(scale(celf5, center = TRUE)),
         celf5.z.c = as.numeric(scale(celf5, scale = TRUE, center = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z.c = as.numeric(scale(tills, scale = TRUE, center = TRUE)))
#manyn400chans_data <- subset(manyn400chans_data, Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6'&celf5>=80)# & Group == "TL")
str(manyn400chans_data )

# Create some data subsets
pic_masked_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "picture" & Prime.Visibility == "masked" & !grepl("^P", Channel))
word_masked_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "word" & Prime.Visibility == "masked" &  !grepl("^FC", Channel))#Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
pic_vis_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "picture" & Prime.Visibility == "visible" & !grepl("^P", Channel))
word_vis_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "word" & Prime.Visibility == "visible" &  !grepl("^FC", Channel))#Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')

# Notes:
# Priming = primed vs. unprimed; default reference level (set above) = unprimed
# ISI = 67 vs. 317; default reference level (set above) = 67
# Experimental Condition = picture vs. word; default reference level = picture
# Stimulus Type = prime vs. target; default reference level = prime (when present)
# Prime Visibility = masked vs. visible; default reference level = masked
# Trial Type = critical vs. probe; default reference level = critical
# Group = DLD vs. TL; default reference level = DLD
```

## Descriptives
```{r}
# N400 mean amplitudes by group, priming condition, experimental condition, and prime visibility (collapsed across region and hemisphere)
manyn400chans_data_grouped1 <- group_by(manyn400chans_data, Experimental.Condition, Prime.Visibility, Group, ISI, Priming)
summarise(manyn400chans_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

manyn400chans_data_grouped1 <- group_by(manyn400chans_data, Experimental.Condition, Prime.Visibility, Group, Priming, ISI)
summarise(manyn400chans_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )


manyn400chans_data_grouped3 <- group_by(manyn400chans_data, Experimental.Condition, Group, Priming)
summarise(manyn400chans_data_grouped3, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

manyn400chans_data_grouped4 <- group_by(manyn400chans_data, Experimental.Condition, Group, ISI)
summarise(manyn400chans_data_grouped4, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

manyn400chans_data_grouped5 <- group_by(manyn400chans_data, Experimental.Condition, Prime.Visibility, Group, ISI)
summarise(manyn400chans_data_grouped5, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

```

## Visualizations
```{r}
word_masked_manyn400chans_data %>%
  mutate(primingxisi = interaction(Priming, ISI, sep = "_"))%>% 
  ggplot(aes(x=primingxisi, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming x ISI")


word_masked_manyn400chans_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=ISI, color=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming")


pic_masked_manyn400chans_data %>%
  mutate(primingxisi = interaction(Priming, ISI, sep = "_"))%>% 
  ggplot(aes(x=ISI, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("Priming x ISI")


celf5_mean <- mean(word_masked_manyn400chans_data$celf5.z.c, na.rm = TRUE)
celf5_sd <- sd(word_masked_manyn400chans_data$celf5.z.c, na.rm = TRUE)
line_position <- celf5_mean - 1.33 * celf5_sd

line_position <- 80

word_masked_manyn400chans_data %>%
  mutate(primingxisi = interaction(Priming, ISI, sep = "_"))%>% 
  ggplot(aes(x=celf5, y=Mean.Amp, group=primingxisi, color=primingxisi,linetype = primingxisi)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  #stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("CELF-5 Core Language Score")+
  geom_vline(xintercept = line_position, linetype = "dashed", color = "black") + # Add vertical line
  geom_smooth(method=lm, aes(linetype = primingxisi))+ 
  scale_color_manual(values = c("primed_67" = "#fb6e29", 
                                "primed_317" = "#38b3e2", 
                                "unprimed_67" = "#fb6e29", 
                                "unprimed_317" = "#38b3e2")) +
  scale_linetype_manual(values = c("primed_67" = "solid", 
                                   "primed_317" = "solid", 
                                   "unprimed_67" = "dashed", 
                                   "unprimed_317" = "dashed")) +
  labs(color = NULL, linetype = NULL) +
  theme_bw() + # Sets the background to white
  theme(text = element_text(family = "Arial", size = 24), 
        axis.title = element_text(face = "bold"),
        legend.position = "none") # Remove the legend

pic_masked_manyn400chans_data %>%
  mutate(primingxisi = interaction(Priming, ISI, sep = "_"))%>% 
  ggplot(aes(x=celf5.z.c, y=Mean.Amp, group=primingxisi, color=primingxisi)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  #stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("CELF-5 CLS")+
  geom_smooth(method=lm)

word_masked_manyn400chans_data %>%
  mutate(primingxisi = interaction(Priming, ISI, sep = "_"))%>% 
  ggplot(aes(x=tills.z.c, y=Mean.Amp, group=primingxisi, color=primingxisi)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  #stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("TILLS")+
  geom_smooth(method=lm)

pic_masked_manyn400chans_data %>%
  mutate(primingxisi = interaction(Priming, ISI, sep = "_"))%>% 
  ggplot(aes(x=tills.z.c, y=Mean.Amp, group=primingxisi, color=primingxisi)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  #stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("TILLS")+
  geom_smooth(method=lm)

```

## Analyses
### Word Data
#### Masked Word Data
CELF Results:
  - significant interaction of priming x ISI x CELF
  - slopes of CELF for primed and unprimed @ 67 and @ 317 ISI are NOT significantly different
  - priming effect (i.e., difference in unprimed and primed mean amps) increases as CELF score increases @ 67 ISI
  - priming effect (i.e., difference in unprimed and primed mean amps) decreases as CELF score increases @ 317 ISI
  - model with CELF variable is better than model with  Group variable
```{r}
# CELF
contrasts(word_masked_manyn400chans_data$Priming)<-contr.sum(levels(word_masked_manyn400chans_data$Priming))/2
contrasts(word_masked_manyn400chans_data$ISI)<-contr.sum(levels(word_masked_manyn400chans_data$ISI))/2
word_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * celf5.z.c + (1|Participant.ID) + (1|Channel),word_masked_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(word_masked_manychans, show.se = TRUE,show.ci = FALSE)

word_masked_emmt <- emtrends(word_masked_manychans, pairwise ~ Priming * ISI, var = "celf5.z.c" )
word_masked_emmt

(mylist <- list(celf5.z.c=c(-1.7,-1,0,1,2.5)))
word_masked_emm  <- emmeans(word_masked_manychans, ~ celf5.z.c* Priming * ISI, at=mylist)
contrast(word_masked_emm, "pairwise",by="celf5.z.c")

word_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * celf5.z.c + (1|Participant.ID) + (1|Channel),word_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
word_masked_manychans_group <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),word_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
anova(word_masked_manychans,word_masked_manychans_group) # model with CELF variable is better than model with  Group variable


# TILLS
contrasts(word_masked_manyn400chans_data$Priming)<-contr.sum(levels(word_masked_manyn400chans_data$Priming))/2
contrasts(word_masked_manyn400chans_data$ISI)<-contr.sum(levels(word_masked_manyn400chans_data$ISI))/2
word_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * tills.z.c + (1|Participant.ID) + (1|Channel),word_masked_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(word_masked_manychans, show.se = TRUE,show.ci = FALSE)

word_masked_emmt <- emtrends(word_masked_manychans, pairwise ~ Priming * ISI, var = "tills.z.c" )
word_masked_emmt

(mylist <- list(tills.z.c=c(-2,-1,0,1,1.7)))
word_masked_emm  <- emmeans(word_masked_manychans, ~ tills.z.c* Priming * ISI, at=mylist)
contrast(word_masked_emm, "pairwise",by="tills.z.c")
```

#### Visible Word Data
Results:
  - Priming (p < .001)
  - ISI (p = .014)
  - ISI x Group (p < .001)
  - Priming x ISI x Group (p = .419 (ns))
    - priming effects for TD kids and kids with DLD at both ISIs (all ps < .002)
```{r}
# word_vis_manychans_red <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),word_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# word_vis_manychans_aug <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1+Priming*ISI|Participant.ID) + (1+Group|Channel),word_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# anova(word_vis_manychans_red,word_vis_manychans_aug)

contrasts(word_vis_manyn400chans_data$Group)<-contr.sum(levels(word_vis_manyn400chans_data$Group))/2
contrasts(word_vis_manyn400chans_data$Priming)<-contr.sum(levels(word_vis_manyn400chans_data$Priming))/2
contrasts(word_vis_manyn400chans_data$ISI)<-contr.sum(levels(word_vis_manyn400chans_data$ISI))/2
word_vis_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),word_vis_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(word_vis_manychans, show.se = TRUE,show.ci = FALSE)

word_vis_emm <- emmeans(word_vis_manychans, pairwise ~ Priming | ISI*Group, adjust = "none")
word_vis_emm
tidy(pairs(word_vis_emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))
```

### Picture Data
#### Masked Picture Data
CELF Results:
  - significant interaction of priming x ISI x CELF
  - slopes of CELF for primed and unprimed @ 67 ISI are significantly different but slopes of CELF for primed and unprimed @ 317 are NOT significantly different
  - priming effect (i.e., difference in unprimed and primed mean amps) initially decreases as CELF score increases until about ~ 1 SD above mean where it increases as CELF score increases as  @ 67 ISI
  - priming effect (i.e., difference in unprimed and primed mean amps) is mostly consistent as CELF score increases @ 317 ISI
  - model with Group variable is about as good as the model with CELF variable
```{r}
# CELF
contrasts(pic_masked_manyn400chans_data$Group)<-contr.sum(levels(pic_masked_manyn400chans_data$Group))/2
contrasts(pic_masked_manyn400chans_data$Priming)<-contr.sum(levels(pic_masked_manyn400chans_data$Priming))/2
contrasts(pic_masked_manyn400chans_data$ISI)<-contr.sum(levels(pic_masked_manyn400chans_data$ISI))/2
pic_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * celf5.z.c + (1|Participant.ID) + (1|Channel),pic_masked_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(pic_masked_manychans, show.se = TRUE,show.ci = FALSE)

pic_masked_emmt <- emtrends(pic_masked_manychans, pairwise ~ Priming * ISI, var = "celf5.z.c" )
pic_masked_emmt

(mylist <- list(celf5.z.c=c(-1.7,-1,0,1,2.5)))
pic_masked_emm  <- emmeans(pic_masked_manychans, ~ celf5.z.c* Priming * ISI, at=mylist)
contrast(pic_masked_emm, "pairwise",by="celf5.z.c")

pic_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * celf5.z.c + (1|Participant.ID) + (1|Channel),pic_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
pic_masked_manychans_group <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),pic_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
anova(pic_masked_manychans,pic_masked_manychans_group) # model with Group variable is about as good as model with CELF variable

# TILLS
contrasts(pic_masked_manyn400chans_data$Group)<-contr.sum(levels(pic_masked_manyn400chans_data$Group))/2
contrasts(pic_masked_manyn400chans_data$Priming)<-contr.sum(levels(pic_masked_manyn400chans_data$Priming))/2
contrasts(pic_masked_manyn400chans_data$ISI)<-contr.sum(levels(pic_masked_manyn400chans_data$ISI))/2
pic_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * tills.z.c + (1|Participant.ID) + (1|Channel),pic_masked_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(pic_masked_manychans, show.se = TRUE,show.ci = FALSE)

pic_masked_emmt <- emtrends(pic_masked_manychans, pairwise ~ Priming * ISI, var = "tills.z.c" )
pic_masked_emmt

(mylist <- list(tills.z.c=c(-1.7,-1,0,1,2.5)))
pic_masked_emm  <- emmeans(pic_masked_manychans, ~ tills.z.c* Priming * ISI, at=mylist)
contrast(pic_masked_emm, "pairwise",by="tills.z.c")
```

#### Visible Picture Data
Results:
  - Priming (p < .001)
  - ISI (p < .001)
  - ISI x Group (p < .001)
  - Priming x ISI x Group (p = .528 (ns))
    - priming effects for TD kids and kids with DLD at both ISIs (all ps < .001)
```{r}
# pic_vis_manychans_red <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),pic_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# pic_vis_manychans_aug <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1+Priming*ISI|Participant.ID) + (1+Priming|Channel),pic_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# anova(pic_vis_manychans_red,pic_vis_manychans_aug)

contrasts(pic_vis_manyn400chans_data$Group)<-contr.sum(levels(pic_vis_manyn400chans_data$Group))/2
contrasts(pic_vis_manyn400chans_data$Priming)<-contr.sum(levels(pic_vis_manyn400chans_data$Priming))/2
contrasts(pic_vis_manyn400chans_data$ISI)<-contr.sum(levels(pic_vis_manyn400chans_data$ISI))/2
pic_vis_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),pic_vis_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(pic_vis_manychans, show.se = TRUE,show.ci = FALSE)

pic_vis_emm <- emmeans(pic_vis_manychans, pairwise ~ Priming | ISI*Group, adjust = "none")
pic_vis_emm
tidy(pairs(pic_vis_emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))
```

# Difference Waves Data (to examine covariates/indiviudal differences)
## Data Manipulations
```{r}
# Load data (3 data frames)
diffwaves_data <- read.csv(here("PADLD Data", "Analysis Data","All PADLD Critical Target Mean Amps (50ms pre post bl many electrodes diff waves).csv"), stringsAsFactors=TRUE) # mean amplitudes of unprimed - primed ERPs from 30 individual electrodes (including the traditional ones) at 300 to 500ms post-target onset for all critical targets (with a +/- 50 ms baseline)

clusterdiffwaves_data <- read.csv(here("PADLD Data", "Analysis Data","PADLD Difference Waves Data (cluster electrode).csv"), stringsAsFactors=TRUE) # mean amplitudes of unprimed - primed ERPs from the average of the 30 individual electrodes

covar_data <- read.csv(here("PADLD Data", "Participant Information","Participant Information & Scores v080824.csv"),stringsAsFactors=TRUE) # behavioral assessment measures

# Format data
diffwaves_data%<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Participant.ID = factor(Participant.ID),
         Channel = factor(Channel),
         ISI = factor(ISI,levels=c("67","317")),
         Experimental.Condition = factor(Experimental.Condition),
         Prime.Visibility = factor (Prime.Visibility),
         Group = factor(Group),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z.c = as.numeric(scale(celf5, scale = TRUE, center = TRUE)),
         age = as.numeric(Average.Age),
         age.z.c = as.numeric(scale(age, scale = TRUE, center = TRUE)),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z.c = as.numeric(scale(nwrppc.arc, scale = TRUE, center = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z.c = as.numeric(scale(nwrpcc.arc, scale = TRUE, center = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z.c = as.numeric(scale(tills, scale = TRUE, center = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z.c = as.numeric(scale(toni, scale = TRUE, center = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z.c = as.numeric(scale(wrmt, scale = TRUE, center = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z.c = as.numeric(scale(flanker, scale = TRUE, center = TRUE)),
         gender.c = as.numeric(Gender) - 1.5,
         Detailed.Language.Status = factor(Detailed.Language.Status),
         Language.Status = factor(Language.Status,levels=c("English monolingual","English primary")),
         langstat.c = as.numeric(Language.Status) - 1.5,
         Bilingual.Type = factor(Bilingual.Type),
         handedness = factor(Handedness),
         hand.c = as.numeric(handedness) - 1.5,
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")),
         pvt.z.c = as.numeric(scale(PVT.Numeric, scale = TRUE, center = TRUE)),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)),
         pvt.z = as.numeric(scale(PVT.Numeric, scale = TRUE)))
str(diffwaves_data)

clusterdiffwaves_data%<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Participant.ID = factor(Participant.ID),
         ISI = factor(ISI,levels=c("67","317")),
         Experimental.Condition = factor(Experimental.Condition),
         Prime.Visibility = factor (Prime.Visibility),
         Group = factor(Group),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z.c = as.numeric(scale(celf5, scale = TRUE, center = TRUE)),
         age = as.numeric(Average.Age),
         age.z.c = as.numeric(scale(age, scale = TRUE, center = TRUE)),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z.c = as.numeric(scale(nwrppc.arc, scale = TRUE, center = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z.c = as.numeric(scale(nwrpcc.arc, scale = TRUE, center = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z.c = as.numeric(scale(tills, scale = TRUE, center = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z.c = as.numeric(scale(toni, scale = TRUE, center = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z.c = as.numeric(scale(wrmt, scale = TRUE, center = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z.c = as.numeric(scale(flanker, scale = TRUE, center = TRUE)),
         gender.c = as.numeric(Gender) - 1.5,
         Detailed.Language.Status = factor(Detailed.Language.Status),
         Language.Status = factor(Language.Status,levels=c("English monolingual","English primary")),
         langstat.c = as.numeric(Language.Status) - 1.5,
         Bilingual.Type = factor(Bilingual.Type),
         handedness = factor(Handedness),
         hand.c = as.numeric(handedness) - 1.5,
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")),
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")),
         pvt.z.c = as.numeric(scale(PVT.Numeric, scale = TRUE, center = TRUE)),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)),
         pvt.z = as.numeric(scale(PVT.Numeric, scale = TRUE)))
str(clusterdiffwaves_data)

# z-score values
covar_data %<>%
  mutate(celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age = as.numeric(Average.Age),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)))
str(covar_data)

# Notes:
# ISI = 67 vs. 317; default reference level (set above) = 67
# Experimental Condition = picture vs. word; default reference level = picture
# Prime Visibility = masked vs. visible; default reference level = masked
# Group = DLD vs. TL; default reference level = DLD
# For gender, female = -0.5 (after centering), male = 0.5 (after centering)
# Detailed Language Status = language status + bilingual type (see below); default reference level= English monolingual
# Language Status = English monolingual vs. English primary; default reference level (set above) \ = English monolingual
# For language status, English monolingual = -0.5 (after centering), English primary/bilingual = 0.5 (after centering)
# Bilingual Type = sequential vs. simultaneous and the languages spoken; default reference level = NA? sequential bilingual (English-French)?
# For handedness, L = -0.5 (after centering), R = 0.5 (after centering)
# PVT = prime visibility threshold (shortest prime duration at which participant identified > 50% of animal primes presented at that duration); 50 vs. 67 vs. 83 vs. 100 vs. 117 vs. > 117; default reference level (set above) = 50
# PVT Numeric = > 117 is replaced with 150 to make the variable closer to continuous rather than catergorical
```

## Analyses
### Word Data
Significant results (when using non-clustered electrodes as DV, i.e., lmer):
 - CELF-5 predicts priming effects for targets following visible primes and a 317-ms ISI (p = .035)
Significant results (when using cluster electrode as DV, i.e., lm):
  - nothing
```{r}
# Create some data subsets
word_masked_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "67")
word_masked_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "317")
word_vis_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "67")
word_vis_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "317")

word_masked_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "67")
word_masked_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "317")
word_vis_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "67")
word_vis_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "317")




word_masked_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" &  !grepl("^FC", Channel) & Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6' & celf5 >= 80)#& Group == "TL")

contrasts(word_masked_diffwaves_data$ISI)<-contr.treatment(levels(word_masked_diffwaves_data$ISI))/2
masked_word_diffwaves <- lmer(Mean.Amp ~ 1 + celf5.z.c*ISI + (1|Participant.ID)+(1|Channel),word_masked_diffwaves_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(masked_word_diffwaves, show.se = TRUE,show.ci = FALSE) 

emm <- emmeans(masked_word_diffwaves, pairwise ~ISI, adjust = "none")
emm
tidy(pairs(emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))

word_masked_diffwaves_data %>%
  ggplot(aes(x=ISI, y=Mean.Amp, group=ISI, color=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  #stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude of Difference Wave") +
  xlab("ISI")+
  geom_smooth(method=lm)

word_masked_diffwaves_data %>%
  ggplot(aes(x=celf5.z.c, y=Mean.Amp, group=ISI, color=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  #stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("CELF-5 CLS")+
  geom_smooth(method=lm)


pic_masked_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" &  !grepl("^P", Channel) & Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')#& Group == "TL")

contrasts(pic_masked_diffwaves_data$ISI)<-contr.treatment(levels(pic_masked_diffwaves_data$ISI))/2
masked_pic_diffwaves <- lmer(Mean.Amp ~ 1 + ISI + (1|Participant.ID),pic_masked_diffwaves_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(masked_pic_diffwaves, show.se = TRUE,show.ci = FALSE) 

pic_masked_diffwaves_data %>%
  ggplot(aes(x=ISI, y=Mean.Amp, group=ISI, color=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  #stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude of Difference Wave") +
  xlab("ISI")+
  geom_smooth(method=lm)





```

### Picture Data
Significant results (when using non-clustered electrodes as DV, i.e., lmer):
 - Gender and participants' prime visibility threshold predicts priming effects for targets following visible primes and a 317-ms ISI (ps = .038 and .046, respectively)
Significant results (when using cluster electrode as DV, i.e., lm):
  - participants' prime visibility threshold predicts priming effects for targets following visible primes and a 317-ms ISI (p = .019)
```{r}
# Create some data subsets
pic_masked_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "67")
pic_masked_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "317")
pic_vis_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "67")
pic_vis_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "317")

pic_masked_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "67")
pic_masked_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "317")
pic_vis_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "67")
pic_vis_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "317")


# Run some regressions
pic_masked_67_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID) + (1|Channel), pic_masked_67_diffwaves_data) 
tab_model(pic_masked_67_covartest)

pic_masked_317_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c+ (1|Participant.ID) + (1|Channel), pic_masked_317_diffwaves_data) 
tab_model(pic_masked_317_covartest)

pic_vis_67_covartest<- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID) + (1|Channel), pic_vis_67_diffwaves_data) 
tab_model(pic_vis_67_covartest)

pic_vis_317_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID), pic_vis_317_diffwaves_data) 
tab_model(pic_vis_317_covartest)


# Compute a correlation matrix of the data rounding to 2 decimal places
pic_masked_67_covar_corr_data <- subset(pic_masked_67_clusterdiffwaves_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','Mean.Amp'))
pic_masked_67_covar_cor <- round(cor(pic_masked_67_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(pic_masked_67_covar_corr_data)

ggcorrplot(
  pic_masked_67_covar_cor,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

# Compute a correlation matrix of the data rounding to 2 decimal places
pic_masked_317_covar_corr_data <- subset(pic_masked_317_clusterdiffwaves_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','Mean.Amp'))
pic_masked_317_covar_corr <- round(cor(pic_masked_317_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(pic_masked_317_covar_corr_data)

ggcorrplot(
  pic_masked_317_covar_corr,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

```


