---
title: "PADLD Analyses 2.0"
author: "Ashlie"
date: "2024-08-03"
output: html_document
---

```{r setup}

# Libraries
pacman::p_load(knitr, # rendering of .Rmd file
               lme4, # model specification/estimation
               afex, # anova and deriving p-values via LRTs from lmer
               broom.mixed, # extracting data from model fits
               faux, # generate correlated values
               tidyverse, # data wrangling and visualization 
               ggridges, # visualization
               viridis, # color schemes for visualization
               kableExtra, # helps with knitting the .Rmd file
               cowplot, # visualization tool to include multiple plots
               ggrain, # visualization tool for raincloud plots
               dplyr, # data manipulation tools
               here, # controlling directories/reproducibility
               tidyr, # formatting package
               readr, # data importation
               Hmisc, # visualization
               emmeans, # estimation of marginal means and contrasts
               sjstats, # estimation of marginal means and contrasts
               lmerTest, # deriving p-values from lmer
               MuMIn, # ?
               sjPlot, # APA formatting of numerical output
               car, # data wrangling and visualization,
               magrittr, # to use %>%
               ggpubr, # ? (Rose had it in her script)
               broom, # ? (Rose had it in her script)
               Matrix, # model specification/estimation,
               multcomp, # multiple comparison adjustments
               forcats, # organizing visualizations
               gtools, # data manipulation/wrangling
               fuzzySim, # FDR correction,
               ez, # anova
               apaTables, # visualization of anova output
               #renv # package versioning/reproducibility
               )

# Global theme set
set.seed(1234) # set random seed for reproducibility

knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)

#theme_set(theme_bw(base_size = 13) + theme(text = element_text(size=13), 
                             #axis.title=element_text(size=12),
                             #strip.text = element_text(margin=margin(2,0,2,0)), 
                             #panel.grid = element_blank()))

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE, fig.width=10, fig.height=8, fig.fullwidth=TRUE)

plot_theme <- 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18), 
        axis.text.x = element_text(size = 13), 
        axis.title.x = element_text(size = 13), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 13),
        strip.background = element_rect(color="white", fill="white", linewidth = 1.5, linetype="solid"))

options(scipen=999)
```
# All Critical Target Data
## Data Manipulation
```{r}
# Load data (2 data frames)
crittarg_data <- read.csv(here("PADLD Data", "Analysis Data","All PADLD Critical Target Mean Amps (50ms pre post bl).csv"),stringsAsFactors=TRUE) # mean amplitudes from 12 individual electrodes at 300 to 500ms post-target onset for all critical targets (with a +/- 50 ms baseline)
#cluster_data <- read.csv(here("PADLD Data", "Analysis Data","PADLD Cluster Electrode Data.csv"),stringsAsFactors=TRUE) # mean amplitudes from a cluster of electrodes at 300 to 500ms post-target onset for all critical targets (with a +/- 50 ms baseline)

crittarg_data %<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Channel = factor(Channel),
         Region = factor(Region, levels=c("frontal","central","parietal","occipital")),
         Hemisphere = factor(Hemisphere, levels=c("left","midline","right")),
         Priming=factor(Priming, levels=c("unprimed","primed")),
         ISI = factor(ISI,levels=c("67","317")),
         Experimental.Condition = factor(Experimental.Condition),
         Stimulus.Type = factor(Stimulus.Type),
         Prime.Visibility = factor (Prime.Visibility),
         Trial.Type = factor(Trial.Type),
         Group = factor(Group))
str(crittarg_data)

# Create some data subsets
piccrittarg_data <- subset(crittarg_data,Experimental.Condition == "picture")
wordcrittarg_data <- subset(crittarg_data,Experimental.Condition == "word")

# Notes:
# Region = anteriority/posteriority; default reference level (set above) = frontal
# Hemisphere = laterality; default reference level (set above) = left
# Priming = primed vs. unprimed; default reference level (set above) = unprimed
# ISI = 67 vs. 317; default reference level (set above) = 67
# Experimental Condition = picture vs. word; default reference level = picture
# Stimulus Type = prime vs. target; default reference level = prime (when present)
# Prime Visibility = masked vs. visible; default reference level = masked
# Trial Type = critical vs. probe; default reference level = critical
# Group = DLD vs. TL; default reference level = DLD
```

## Descriptives
```{r}
# N400 mean amplitudes by group, priming condition, experimental condition, and prime visibility (collapsed across region and hemisphere)
crittarg_data_grouped1 <- group_by(crittarg_data, Experimental.Condition, Group, Prime.Visibility, Priming, ISI)
summarise(crittarg_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

# N400 mean amplitudes by group, priming condition, experimental condition, and prime visibility
crittarg_data_grouped2 <- group_by(crittarg_data, Experimental.Condition, Group, Prime.Visibility, Priming, ISI, Region, Hemisphere)
summarise(crittarg_data_grouped2, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )
```

## Visualizations
```{r}
##### SINGLE FACTOR VISUALIZATIONS #####

# N400 mean amplitude by (collapsed across experimental condition, group, prime visibility, priming condition, region, and hemisphere)
hist(crittarg_data$Mean.Amp)
boxplot(crittarg_data$Mean.Amp)

# N400 mean amplitude by experimental condition (collapsed across group, prime visibility, priming condition, region, and hemisphere)
plot(Mean.Amp ~ Experimental.Condition, data = crittarg_data)

# N400 mean amplitude by group (collapsed acrossexperimental condition, prime visibility, priming condition, region, and hemisphere)
plot(Mean.Amp ~ Group, data = crittarg_data)


#### GROUP x PRIMING ####

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")


#### GROUP x PRIMING x ISI ####

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for masked picture data
maskedpic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Picture Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for masked word data
maskedword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Word Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for visible picture data
vispic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Picture Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for visible picture data
visword_data <- subset(wordcrittarg_data, Prime.Visibility == "visible")
visword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Word Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)


#### GROUP x PRIMING x REGION ####

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for masked picture data
maskedpic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Picture Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for masked word data
maskedword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Word Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for visible picture data
vispic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Picture Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 ffacet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for visible picture data
visword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Word Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

#### GROUP x PRIMING x ISI x HEMISPHERE ####

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
 facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
 facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
 facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)


#### GROUP x PRIMING x ISI x REGION ####

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

#### GROUP x PRIMING x ISI x HEMISPHERE x REGION ####

# N400 mean amplitude by group and priming condition and hemisphere and region for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)



maskedword_data <- subset(wordcrittarg_data, Prime.Visibility == "masked")
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=interaction(ISI, Group),  color=Group, shape=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") #+
  #facet_wrap(~Group)


visword_data <- subset(wordcrittarg_data, Prime.Visibility == "visible")
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp,  group=interaction(ISI, Group), color=Group, shape=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") #+
  #facet_wrap(~Group)


```

## Analyses
### Omnibus ANOVAs (overall differences)
#### Words
Results:
- significant effects (only reporting results from post-hoc emmeans tests that are significant after correcting for multiple comparisons, i.e., < .05/however many comparisons in that emmean test, but reporting unadjusted p-values):
  - ISI (p < .001) 
    - more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI
  - Priming x Region (p = .014) 
    - driven by typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) in central region (p = .002)
  - ISI x Region (p = .010) 
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in frontal (p < .001) and central regions (p < .001)
  - ISI x Prime Visibility x Region (p < .001)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI for targets following masked primes in frontal (p < .001), central (p < .001), and parietal regions (p < .004)
  - ISI x Prime Visibility x Hemisphere (p = .006)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI for targets following masked primes in left, midline, and right hemispheres (all ps < .001)
```{r}
options(contrasts = c("contr.sum", "contr.poly")) # contrast code doesn't work without this but you don't need it to just run the anova
wordanova <-ezANOVA(data=wordcrittarg_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Prime.Visibility,Region,Hemisphere), # within-subjects variable
        type=3,
        return_aov=TRUE) # because i need this for  post hocs
wordanova_table <- apa.ezANOVA.table(wordanova)
print(wordanova)

wordemm1 <- emmeans(wordanova$aov, ~ ISI)
wordemm1

wordemm2 <- emmeans(wordanova$aov, ~ Priming | Region)
wordemm2
tidy(pairs(wordemm2, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

wordemm3 <- emmeans(wordanova$aov, ~ ISI | Region)
wordemm3
tidy(pairs(wordemm3, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

wordemm4 <- emmeans(wordanova$aov, ~ ISI| Prime.Visibility*Region)
wordemm4
tidy(pairs(wordemm4, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

wordemm5 <- emmeans(wordanova$aov, ~ ISI | Prime.Visibility*Hemisphere)
wordemm5
tidy(pairs(wordemm5, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))
```

##### DLD
Results:
- significant effects (only reporting results from post-hoc emmeans tests that are significant after correcting for multiple comparisons, i.e., < .05/however many comparisons in that emmean test, but reporting unadjusted p-values):
  - ISI (p = .041)
    - more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI
  - Region (p = .009) - not interested
  - Prime Visibility x Region (p = .043)
    - driven by more negative N400 mean amplitudes for targets following masked primes than targets following visible primes in frontal region (p = .001)
- although no interaction with priming is significant, a priori hypotheses about priming and ISI (and prime visiblity), so exploring simple effects anyway
  - no significant differences between priming conditions (even when include prime visibility, region, and/or hemisphere) when corrected for multiple comparisons (although typical priming effect for the 67-ms ISI for targets following visible primes in the right occipital region based on unadjusted p-value (p = .044))
```{r}
options(contrasts = c("contr.sum", "contr.poly")) # contrast code doesn't work without this but you don't need it to just run the anova
dldwordanova <-ezANOVA(data=subset(wordcrittarg_data,Group=="DLD"),
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Prime.Visibility,Region,Hemisphere), # within-subjects variable
        type=3,
        return_aov=TRUE) # because i need this for  post hocs
dldwordanova_table <- apa.ezANOVA.table(dldwordanova)
print(dldwordanova)

dldwordemm1 <- emmeans(dldwordanova$aov, ~ ISI)
dldwordemm1

dldwordemm2 <- emmeans(dldwordanova$aov, ~ Prime.Visibility | Region)
dldwordemm2
tidy(pairs(dldwordemm2, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

dldwordemm3 <- emmeans(dldwordanova$aov, ~ Priming | ISI*Prime.Visibility*Region*Hemisphere)
dldwordemm3
tidy(pairs(dldwordemm3, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))
```

##### TL
Results:
- significant effects (only reporting results from post-hoc emmeans tests that are significant after correcting for multiple comparisons, i.e., < .05/however many comparisons in that emmean test, but reporting unadjusted p-values):
  - ISI (p = .001)
    - more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI
  - Region (p < .001) - not interested
  - ISI x Region (p = .005)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in frontal and central regions (both ps < .001)
  - Priming x Hemisphere (p = .020)
    - driven by typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) in right hemisphere (p = .016)
  - ISI x Prime Visibility x Region (p < .001)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI for targets following masked primes in frontal and central regions (both ps < .001)
  - ISI x Prime Visibility x Hemisphere (p = .017)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in left, midline, and right hemispheres (all ps < .001)
- although no interaction with priming besides priming x hemisphere is significant, a priori hypotheses about priming and ISI (and prime visibility), so exploring simple effects anyway
  - no significant differences between priming conditions (even when include prime visibility, region, and/or hemisphere) when corrected for multiple comparisons (although handful of significant differences between priming conditions at different ISIs/visiblities/regions/hemispheres based on unadjusted p-values)
```{r}
options(contrasts = c("contr.sum", "contr.poly")) # contrast code doesn't work without this but you don't need it to just run the anova
tlwordanova <-ezANOVA(data=subset(wordcrittarg_data,Group=="TL"),
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Prime.Visibility,Region,Hemisphere), # within-subjects variable
        type=3,
        return_aov=TRUE) # because i need this for  post hocs
tlwordanova_table <- apa.ezANOVA.table(tlwordanova)
print(tlwordanova)

tlwordemm1 <- emmeans(tlwordanova$aov, ~ ISI)
tlwordemm1

tlwordemm2 <- emmeans(tlwordanova$aov, ~ ISI | Region)
tlwordemm2
tidy(pairs(tlwordemm2, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlwordemm3 <- emmeans(tlwordanova$aov, ~ Priming | Hemisphere)
tlwordemm3
tidy(pairs(tlwordemm3, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlwordemm4 <- emmeans(tlwordanova$aov, ~ ISI| Prime.Visibility*Region)
tlwordemm4
tidy(pairs(tlwordemm4, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlwordemm5 <- emmeans(tlwordanova$aov, ~ ISI | Prime.Visibility*Hemisphere)
tlwordemm5
tidy(pairs(tlwordemm5, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlwordemm6 <- emmeans(tlwordanova$aov, ~ Priming | ISI*Prime.Visibility*Region)
tlwordemm6
tidy(pairs(tlwordemm6, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

```


#### Pictures
Results:
- significant effects (only reporting results from post-hoc emmeans tests that are significant after correcting for multiple comparisons, i.e., < .05/however many comparisons in that emmean test, but reporting unadjusted p-values):
  - Priming (p = .036)
    - typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed)
  - ISI (p = .021)
    - more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI
  - Region (p < .001) - uninterested in this
  - Hemisphere (p = .006) - uninterested in this
  - Priming x Region (p < .001)
    - driven by typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) in frontal and central regions (both ps < .001) but reversed effect in occipital region (p = .002)
  - ISI x Region (p < .001)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in occipital region (p < .001)
  - Prime Visibility x Region (p = .001)
   - driven by more N400 mean amplitudes for targets following visible primes than masked primes in central region (p = .012) but reversed in occipital region (p = .002)
  - Priming x Hemisphere (p = .015)
    - driven by typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) in midline (p = .013) and right hemisphere (p = .008)
  - ISI x Hemisphere (p = .002)
   - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in right hemisphere (p < .001)
  - Region x Hemisphere (p < .001) - uninterested in this
  - Priming x Prime Visibility x Region (p = .035)
    - driven by typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) for targets following masked primes in frontal region (p = .003) and for targets following visible primes in frontal and central  regions (all ps < .001) but reversed effect for targets following visible primes in occipital region (p < .001)
  - ISI x Prime Visibility x Region (p < .001)
    - driven by more negative N400 me an amplitudes for 67-ms ISI than 317-ms ISI for targets following masked primes in frontal (p < .001), central (p < .001), and occipital  ( p = .004) regions and for targets following visible primes in occipital region (p < .001) but reversed effect for targets following visible primes in frontal and central regions (both ps < .001)
  - ISI x Prime Visibility x Region x Hemisphere (p = .011)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI for targets following masked primes in left frontal and central, midline frontal and central, and right frontal, central, and occipital regions (all ps < .001, except right occipital: p = .002) and for targets following visible primes in left occipital, midline occipital, and right occipital regions (all ps < .001) but reversed for for targets following visible primes in left frontal and central, midline frontal and central, and right frontal and central regions (all ps < .001)
```{r}
options(contrasts = c("contr.sum", "contr.poly")) # contrast code doesn't work without this but you don't need it to just run the anova
picanova <-ezANOVA(data=piccrittarg_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Prime.Visibility,Region,Hemisphere), # within-subjects variable
        type=3,
        return_aov=TRUE) # because i need this for  post hocs
picanova_table <- apa.ezANOVA.table(picanova)
print(picanova)

picemm1 <- emmeans(picanova$aov, ~ Priming)
picemm1

picemm2 <- emmeans(picanova$aov, ~ ISI)
picemm2

picemm3 <- emmeans(picanova$aov, ~ Priming | Region)
picemm3
tidy(pairs(picemm3, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

picemm4 <- emmeans(picanova$aov, ~ ISI | Region)
picemm4
tidy(pairs(picemm4, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

picemm5 <- emmeans(picanova$aov, ~ Prime.Visibility | Region)
picemm5
tidy(pairs(picemm5, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

picemm6 <- emmeans(picanova$aov, ~ Priming | Hemisphere)
picemm6
tidy(pairs(picemm6, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

picemm7 <- emmeans(picanova$aov, ~ ISI | Hemisphere)
picemm7
tidy(pairs(picemm7, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

picemm8 <- emmeans(picanova$aov, ~ Priming | Prime.Visibility*Region)
picemm8
tidy(pairs(picemm8, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

picemm9 <- emmeans(picanova$aov, ~ ISI | Prime.Visibility*Region)
picemm9
tidy(pairs(picemm9, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

picemm10 <- emmeans(picanova$aov, ~ ISI | Prime.Visibility*Region*Hemisphere)
picemm10
pairs(picemm10, adjust="none")
tidy(pairs(picemm10, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

```

##### DLD
Results:
- significant effects (only reporting results from post-hoc emmeans tests that are significant after correcting for multiple comparisons, i.e., < .05/however many comparisons in that emmean test, but reporting unadjusted p-values):
  - Region (p = .012) - not interested
  - Priming x Region (p = .031)
    - no significant differences between priming conditions when corrected for multiple comparisons (although typical priming effect in the central region (p = .013) and reversed effect in occipital region (p = .039) based on unadjusted p-values)
  - ISI x Region (p = .013)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in occipital region (p < .001)
  - Region x Hemisphere (.012) - not interested
- although no interaction with priming is significant, a priori hypotheses about priming and ISI (and prime visiblity), so exploring simple effects anyway
  - typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) for 317 ISI for targets following visible primes in central midline region (p < .001), otherwise no significant differences between priming conditions (even when include prime visibility, region, and/or hemisphere) when corrected for multiple comparisons (although handful of significant differences between priming conditions at different ISIs/visiblities/regions/hemispheres based on unadjusted p-values)
```{r}
options(contrasts = c("contr.sum", "contr.poly")) # contrast code doesn't work without this but you don't need it to just run the anova
dldpicanova <-ezANOVA(data=subset(piccrittarg_data,Group=="DLD"),
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Prime.Visibility,Region,Hemisphere), # within-subjects variable
        type=3,
        return_aov=TRUE) # because i need this for  post hocs
dldpicanova_table <- apa.ezANOVA.table(dldpicanova)
print(dldpicanova)

dldpicemm1 <- emmeans(dldpicanova$aov, ~ Priming | Region)
dldpicemm1
tidy(pairs(dldpicemm1, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

dldpicemm2 <- emmeans(dldpicanova$aov, ~ ISI | Region)
dldpicemm2
tidy(pairs(dldpicemm2, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

dldpicemm3 <- emmeans(dldpicanova$aov, ~ Priming | ISI*Prime.Visibility*Region*Hemisphere)
dldpicemm3
tidy(pairs(dldpicemm3, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))
```

##### TL
Results:
- significant effects (only reporting results from post-hoc emmeans tests that are significant after correcting for multiple comparisons, i.e., < .05/however many comparisons in that emmean test, but reporting unadjusted p-values):
  - Region (p < .001) - not interested
  - Hemisphere (p = 019) - not interested
  - Priming x Region (p < .001)
    - driven by typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) in frontal and central regions (both ps < .001)
  - ISI x Region (p = .002)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in occipital region (p < .001)
  - Prime Visibility x Region (p = .011)
    - no significant differences between prime visiblity conditions when corrected for multiple comparisons
  - Priming x Hemisphere (p = .020)
    - driven by typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) in right hemisphere (p = .014)
  - ISI x Hemisphere (p = .014)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI in right hemisphere (p = .006)
  - Region x Hemisphere (p < .001) - not interested
  - ISI x Prime Visibility x Region (p < .001)
    - driven by more negative N400 mean amplitudes for 67-ms ISI than 317-ms ISI for targets following masked primes in frontal and central regions (both ps < .001) and for targets following visible primes in frontal and central regions but a reversed effect in occipital region (all ps < .001)
  - ISI x Prime Visibility x Region x Hemisphere (p = .011)
    - driven by a whole bunch of significant differences between ISIs at all sorts of region and hemisphere combos (all ps < .001), but this isn't really relevant to my research questions so I'm not going to bother writing out all the significant differences
- although no interaction with priming besides priming x hemisphere is significant, a priori hypotheses about priming and ISI (and prime visibility), so exploring simple effects anyway
  - fair amount of significant differences between priming conditions (even when include prime visibility, region, and/or hemisphere and when corrected for multiple comparisons)
   - typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) for 317 ISI overall (p = .022)
   - typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) for 317 ISI in the midline (p = .008) and right hemisphere (p = .006)
   -  typical priming effect (i.e., more negative N400 mean amplitudes for unprimed than primed) for 317 ISI for targets following visible primes in the frontal (p < .001) and central regions (p = .002)
   - more too, but too tired to write them all out right now and not sure whether this analysis even matters
```{r}
options(contrasts = c("contr.sum", "contr.poly")) # contrast code doesn't work without this but you don't need it to just run the anova
tlpicanova <-ezANOVA(data=subset(piccrittarg_data,Group=="TL"),
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Prime.Visibility,Region,Hemisphere), # within-subjects variable
        type=3,
        return_aov=TRUE) # because i need this for  post hocs
tlpicanova_table <- apa.ezANOVA.table(tlpicanova)
print(tlpicanova)

tlpicemm1 <- emmeans(tlpicanova$aov, ~ Priming | Region)
tlpicemm1
tidy(pairs(tlpicemm1, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlpicemm2 <- emmeans(tlpicanova$aov, ~ ISI | Region)
tlpicemm2
tidy(pairs(tlpicemm2, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlpicemm3 <- emmeans(tlpicanova$aov, ~ Prime.Visibility | Region)
tlpicemm3
tidy(pairs(tlpicemm3, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlpicemm4 <- emmeans(tlpicanova$aov, ~ Priming | Hemisphere)
tlpicemm4
tidy(pairs(tlpicemm4, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlpicemm5 <- emmeans(tlpicanova$aov, ~ ISI | Hemisphere)
tlpicemm5
tidy(pairs(tlpicemm5, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlpicemm6 <- emmeans(tlpicanova$aov, ~ ISI | Prime.Visibility*Region)
tlpicemm6
tidy(pairs(tlpicemm6, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlpicemm7 <- emmeans(tlpicanova$aov, ~ ISI | Prime.Visibility*Region*Hemisphere)
tlpicemm7
tidy(pairs(tlpicemm7, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

tlpicemm8 <- emmeans(tlpicanova$aov, ~ Priming | ISI*Prime.Visibility*Region*Hemisphere)
tlpicemm8
tidy(pairs(tlpicemm8, adjust="none"))%>%
   mutate(signif = stars.pval(p.value))

```



### Post-ominbus ANOVA DLD vs. TL comparison analyses (lmers with cluser electrodes)
#### DLD
##### Masked Words
```{r}
```
##### Masked Pictures
```{r}
```
##### Visible Words
```{r}
```
##### Visible Pictures
```{r}
```

#### TL
##### Masked Words
```{r}
```
##### Masked Pictures
```{r}
```
##### Visible Words
```{r}
```
##### Visible Pictures
```{r}
```
