---
title: "PADLD Analyses 3.0"
author: "Ashlie"
date: "2024-08-08"
output: html_document
---

```{r setup}

# Libraries
pacman::p_load(knitr, # rendering of .Rmd file
               lme4, # model specification/estimation
               afex, # anova and deriving p-values via LRTs from lmer
               broom.mixed, # extracting data from model fits
               faux, # generate correlated values
               tidyverse, # data wrangling and visualization 
               ggridges, # visualization
               viridis, # color schemes for visualization
               kableExtra, # helps with knitting the .Rmd file
               cowplot, # visualization tool to include multiple plots
               ggrain, # visualization tool for raincloud plots
               dplyr, # data manipulation tools
               here, # controlling directories/reproducibility
               tidyr, # formatting package
               readr, # data importation
               Hmisc, # visualization
               emmeans, # estimation of marginal means and contrasts
               sjstats, # estimation of marginal means and contrasts
               lmerTest, # deriving p-values from lmer
               MuMIn, # ?
               sjPlot, # APA formatting of numerical output
               car, # data wrangling and visualization,
               magrittr, # to use %>%
               ggpubr, # ? (Rose had it in her script)
               broom, # ? (Rose had it in her script)
               Matrix, # model specification/estimation,
               multcomp, # multiple comparison adjustments
               forcats, # organizing visualizations
               gtools, # data manipulation/wrangling
               fuzzySim, # FDR correction,
               ez, # anova
               apaTables, # visualization of anova output
               #renv # package versioning/reproducibility
               )

# Global theme set
set.seed(1234) # set random seed for reproducibility

knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)

#theme_set(theme_bw(base_size = 13) + theme(text = element_text(size=13), 
                             #axis.title=element_text(size=12),
                             #strip.text = element_text(margin=margin(2,0,2,0)), 
                             #panel.grid = element_blank()))

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE, fig.width=10, fig.height=8, fig.fullwidth=TRUE)

plot_theme <- 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18), 
        axis.text.x = element_text(size = 13), 
        axis.title.x = element_text(size = 13), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 13),
        strip.background = element_rect(color="white", fill="white", linewidth = 1.5, linetype="solid"))

options(scipen=999)
```

# Demographic and Behavioral Assessment Data
## Data Manipulations
```{r}
# Load data (2 data frames)
demobehav_data <- read.csv(here("PADLD Data", "Participant Information","Participant Information & Scores v080824.csv"),stringsAsFactors=TRUE) # demographic data and behavioral assessment measures
ar_data <- read.csv(here("PADLD Data", "Analysis Data","AR Data.csv"),stringsAsFactors=TRUE) #artifact rejection data

# Format data
demobehav_data %<>%
  mutate(Group = factor(Group),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z.c = as.numeric(scale(celf5, scale = TRUE, center = TRUE)),
         age = as.numeric(Average.Age),
         age.z.c = as.numeric(scale(age, scale = TRUE, center = TRUE)),
         nwrppc = as.numeric(NWR.PPC),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z.c = as.numeric(scale(nwrppc.arc, scale = TRUE, center = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z.c = as.numeric(scale(nwrpcc.arc, scale = TRUE, center = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z.c = as.numeric(scale(tills, scale = TRUE, center = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z.c = as.numeric(scale(toni, scale = TRUE, center = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z.c = as.numeric(scale(wrmt, scale = TRUE, center = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z.c = as.numeric(scale(flanker, scale = TRUE, center = TRUE)),
         gender = factor(Gender),
         gender.c = as.numeric(Gender) - 1.5,
         Detailed.Language.Status = factor(Detailed.Language.Status),
         Language.Status = factor(Language.Status,levels=c("English monolingual","English primary")),
         langstat.c = as.numeric(Language.Status) - 1.5,
         Bilingual.Type = factor(Bilingual.Type),
         handedness = factor(Handedness),
         hand.c = as.numeric(handedness) - 1.5,
         pvt.word = factor(PVT.word,levels=c("50","67","83","100","> 117")),
         pvt.pic = factor(PVT.pic,levels=c("50","67","83","100","> 117")),
         pvt.word.z.c = as.numeric(scale(PVT.word.numeric, scale = TRUE, center = TRUE)),
         pvt.pic.z.c = as.numeric(scale(PVT.pic.numeric, scale = TRUE, center = TRUE)),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)),
         pvt.word.z = as.numeric(scale(PVT.word.numeric, scale = TRUE)),
         pvt.pic.z = as.numeric(scale(PVT.pic.numeric, scale = TRUE)),
         total.components.removed = as.numeric(total.components.removed),
         total.chans.interp = as.numeric(total.chans.interp))
str(demobehav_data)

# Format data
ar_data %<>%
  mutate(Group = factor(Group),
         totalperrej = as.numeric(totalperrej),
         Condition = factor(Condition))

# Create some data subsets
demobehav_data <- subset(demobehav_data, Exclude. != "Yes")

# Notes:
# Group = DLD vs. TL; default reference level = DLD
# For gender, female = -0.5 (after centering), male = 0.5 (after centering)
# Detailed Language Status = language status + bilingual type (see below); default reference level= English monolingual
# Language Status = English monolingual vs. English primary; default reference level (set above) \ = English monolingual
# For language status, English monolingual = -0.5 (after centering), English primary/bilingual = 0.5 (after centering)
# Bilingual Type = sequential vs. simultaneous and the languages spoken; default reference level = NA? sequential bilingual (English-French)?
# For handedness, L = -0.5 (after centering), R = 0.5 (after centering)
# PVT = prime visibility threshold (shortest prime duration at which participant identified > 50% of animal primes presented at that duration); 50 vs. 67 vs. 83 vs. 100 vs. 117 vs. > 117; default reference level (set above) = 50
# PVT Numeric = > 117 is replaced with 150 to make the variable closer to continuous rather than catergorical
```

## Descriptives
```{r}
# CELF-5 CLS
demobehav_data_celf5 <- group_by(demobehav_data, Group)
summarise(demobehav_data_celf5, # summarize operation by group
  mean = mean(celf5),
  std = sd(celf5)
    )

# age
demobehav_data_age <- group_by(demobehav_data, Group)
summarise(demobehav_data_age, # summarize operation by group
  mean = mean(age),
  std = sd(age)
    )

# NWR (PPC)
demobehav_data_nwrppc <- group_by(demobehav_data, Group)
summarise(demobehav_data_nwrppc, # summarize operation by group
  mean = mean(nwrppc),
  std = sd(nwrppc)
    )

# TILLS
demobehav_data_tills <- group_by(demobehav_data, Group)
summarise(demobehav_data_tills, # summarize operation by group
  mean = mean(tills),
  std = sd(tills)
    )

# TONI
demobehav_data_toni <- group_by(demobehav_data, Group)
summarise(demobehav_data_toni, # summarize operation by group
  mean = mean(toni),
  std = sd(toni)
    )

# WRMT
demobehav_data_wrmt <- group_by(demobehav_data, Group)
summarise(demobehav_data_wrmt, # summarize operation by group
  mean = mean(wrmt),
  std = sd(wrmt)
    )

# Flanker
demobehav_data_flanker <- group_by(demobehav_data, Group)
summarise(demobehav_data_flanker, # summarize operation by group
  mean = mean(flanker),
  std = sd(flanker)
    )

# gender
demobehav_data_gender <- group_by(demobehav_data, Group,gender)
demobehav_data_gender %>%
  tally()

# language status
demobehav_data_langstat <- group_by(demobehav_data, Group,Language.Status)
demobehav_data_langstat %>%
  tally()

# handedness
demobehav_data_handedness <- group_by(demobehav_data, Group,handedness)
demobehav_data_handedness %>%
  tally()

# PVT word
demobehav_data_pvt.word <- group_by(demobehav_data, Group,pvt.word)
demobehav_data_pvt.word %>%
  tally()

# PVT word
demobehav_data_pvt.pic <- group_by(demobehav_data, Group,pvt.pic)
demobehav_data_pvt.pic %>%
  tally()
```

## Analyses
```{r}
# CELF-5 CLS
demobehav_celf5 <- t.test(celf5.z ~ Group, data = demobehav_data)
demobehav_celf5

# age
demobehav_age <- t.test(age ~ Group, data = demobehav_data)
demobehav_age

# NWR (PPC)
demobehav_nwrppc <- t.test(nwrppc.arc.z ~ Group,demobehav_data)
demobehav_nwrppc

# TILLS
demobehav_tills <- t.test(tills.z ~ Group,demobehav_data)
demobehav_tills

# TONI
demobehav_toni <- t.test(toni.z ~ Group,demobehav_data)
demobehav_toni

# WRMT
demobehav_wrmt <- t.test(wrmt.z  ~ Group,demobehav_data)
demobehav_wrmt

# Flanker
demobehav_flanker <- t.test(flanker.z  ~ Group,demobehav_data)
demobehav_flanker

# PVT Word
demobehav_pvtword <- t.test(pvt.word.z  ~ Group,demobehav_data)
demobehav_pvtword

# PVT Pic
demobehav_pvtpic <- t.test(pvt.pic.z  ~ Group,demobehav_data)
demobehav_pvtword

# components removed
demobehav_comprem <- t.test(total.components.removed  ~ Group,demobehav_data)
demobehav_comprem

# channels interpolated
demobehav_chaninterp <- t.test(total.chans.interp  ~ Group,demobehav_data)
demobehav_chaninterp

# epochs rejected
ar_data_model <- lmer(totalperrej ~ 1 + Group*Condition + (1|Participant.ID),ar_data)
tab_model(ar_data_model, show.se = TRUE, show.ci = FALSE)

emm <- emmeans(ar_data_model, pairwise ~ Condition | Group, adjust = "none")
emm
tidy(pairs(emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))

```

# Behavioral Response Data
## Data Manipulations
```{r}
# Load data
behavresp_data <- read.csv(here("PADLD Data", "Analysis Data","Behavioral Response Data.csv"), stringsAsFactors=TRUE) # behavioral response data

# Format data
behavresp_data %<>%
  mutate(Percent.ID = as.numeric(Percent.ID),
         perid.arc = asin(sqrt(as.numeric(Percent.ID)/100)),
         Participant.ID = factor(Participant.ID),
         Stimulus = factor(Stimulus),
         Prime.Visibility = factor (Prime.Visibility),
         Experimental.Condition = factor (Experimental.Condition),
         ISI = factor(ISI),
         Group = factor(Group))
str(behavresp_data)

# Create some subsets
masked_behavresp_data <- subset(behavresp_data,Prime.Visibility == "Mask")
```

## Descriptives
```{r}
behavresp_data_grouped1 <- group_by(behavresp_data, Experimental.Condition, Group, Prime.Visibility, Stimulus, ISI)
summarise(behavresp_data_grouped1, # summarize operation by group
  mean = mean(Percent.ID),
  std = sd(Percent.ID)
    )

behavresp_data_grouped2 <- group_by(behavresp_data, Experimental.Condition, Group, Prime.Visibility, Stimulus)
summarise(behavresp_data_grouped2, # summarize operation by group
  mean = mean(Percent.ID),
  std = sd(Percent.ID)
    )

behavresp_data_grouped3 <- group_by(behavresp_data, Experimental.Condition, Prime.Visibility, Stimulus)
summarise(behavresp_data_grouped3, # summarize operation by group
  mean = mean(Percent.ID),
  std = sd(Percent.ID)
    )

```


## Analyses
```{r}
contrasts(masked_behavresp_data$Group)<-contr.sum(levels(masked_behavresp_data$Group))/2
contrasts(masked_behavresp_data$Stimulus)<-contr.sum(levels(masked_behavresp_data$Stimulus))/2
contrasts(masked_behavresp_data$Experimental.Condition)<-contr.sum(levels(masked_behavresp_data$Experimental.Condition))/2
contrasts(masked_behavresp_data$ISI)<-contr.sum(levels(masked_behavresp_data$ISI))/2

masked_behavresp_model <- lmer(perid.arc ~ 1 + Group*Stimulus*Experimental.Condition*ISI + (1|Participant.ID), masked_behavresp_data) 
tab_model(masked_behavresp_model)

masked_behavresp_emm1 <- emmeans(masked_behavresp_model, pairwise ~ Group | Stimulus*Experimental.Condition, adjust = "none")
masked_behavresp_emm1
tidy(pairs(masked_behavresp_emm1, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))

masked_behavresp_emm4 <- emmeans(masked_behavresp_model, pairwise ~ Group | Stimulus*Experimental.Condition*ISI, adjust = "none")
masked_behavresp_emm4
tidy(pairs(masked_behavresp_emm4, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))


masked_behavresp_emm2 <- emmeans(masked_behavresp_model, pairwise ~  Stimulus | Experimental.Condition*Group, adjust = "none")
masked_behavresp_emm2
tidy(pairs(masked_behavresp_emm2, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))


masked_behavresp_emm3 <- emmeans(masked_behavresp_model, pairwise ~  Stimulus | Experimental.Condition*ISI*Group, adjust = "none")
masked_behavresp_emm3
tidy(pairs(masked_behavresp_emm3, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))


```

# Few N400 Channels Data (to examine overall effects)
## Data Manipulation
```{r}
# Load data
fewn400chans_data <- read.csv(here("PADLD Data", "Analysis Data","All PADLD Critical Target Mean Amps (50ms pre post bl).csv"),stringsAsFactors=TRUE) # mean amplitudes from 12 electrodes used to measure the N400 at 300 to 500ms post-target onset for all critical targets (with a +/- 50 ms baseline)

# Data from electrodes traditionally used to measure N400 
fewn400chans_data %<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Participant.ID = factor(Participant.ID),
         Channel = factor(Channel),
         Region = factor(Region, levels=c("frontal","central","parietal","occipital")),
         Hemisphere = factor(Hemisphere, levels=c("left","midline","right")),
         Priming=factor(Priming, levels=c("unprimed","primed")),
         Priming.c = as.numeric(Priming) - 1.5,
         ISI = factor(ISI,levels=c("67","317")),
         ISI.c = as.numeric(ISI) - 1.5,
         Experimental.Condition = factor(Experimental.Condition),
         Experimental.Condition.c = as.numeric(Experimental.Condition) - 1.5,
         Stimulus.Type = factor(Stimulus.Type),
         Prime.Visibility = factor (Prime.Visibility),
         Prime.Visibility.c = as.numeric(Prime.Visibility) - 1.5,
         Trial.Type = factor(Trial.Type),
         Group = factor(Group, levels=c("TL","DLD")),
         Group.c = as.numeric(Group) - 1.5)
str(fewn400chans_data)

# Create some data subsets
pic_fewn400chans_data <- subset(fewn400chans_data,Experimental.Condition == "picture")
word_fewn400chans_data <- subset(fewn400chans_data,Experimental.Condition == "word")

# Notes:
# Region = anteriority/posteriority; default reference level (set above) = frontal
# Hemisphere = laterality; default reference level (set above) = left
# Priming = primed vs. unprimed; default reference level (set above) = unprimed
# ISI = 67 vs. 317; default reference level (set above) = 67
# Experimental Condition = picture vs. word; default reference level = picture
# Stimulus Type = prime vs. target; default reference level = prime (when present)
# Prime Visibility = masked vs. visible; default reference level = masked
# Trial Type = critical vs. probe; default reference level = critical
# Group = DLD vs. TL; default reference level = DLD
```

## Descriptives
```{r}
# N400 mean amplitudes by group, priming condition, experimental condition, and prime visibility (collapsed across region and hemisphere)
fewn400chans_data_grouped1 <- group_by(fewn400chans_data, Experimental.Condition, Prime.Visibility, ISI, Priming)
summarise(fewn400chans_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

fewn400chans_data_grouped2 <- group_by(fewn400chans_data, Experimental.Condition, Prime.Visibility)
summarise(fewn400chans_data_grouped2, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

fewn400chans_data_grouped3 <- group_by(fewn400chans_data, Experimental.Condition, Priming)
summarise(fewn400chans_data_grouped3, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

fewn400chans_data_grouped4 <- group_by(fewn400chans_data, Experimental.Condition, ISI)
summarise(fewn400chans_data_grouped4, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

fewn400chans_data_grouped5 <- group_by(fewn400chans_data, Experimental.Condition, Prime.Visibility, ISI)
summarise(fewn400chans_data_grouped5, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

```

## Visualizations
```{r}

##### SINGLE FACTOR VISUALIZATIONS #####

# N400 mean amplitude by (collapsed across experimental condition, group, prime visibility, priming condition, region, and hemisphere)
hist(fewn400chans_data$Mean.Amp)
boxplot(fewn400chans_data$Mean.Amp)

# N400 mean amplitude by experimental condition (collapsed across group, prime visibility, priming condition, region, and hemisphere)
plot(Mean.Amp ~ Experimental.Condition, data = fewn400chans_data)

# N400 mean amplitude by group (collapsed across experimental condition, prime visibility, priming condition, region, and hemisphere)
plot(Mean.Amp ~ Group, data = fewn400chans_data)


#### GROUP x PRIMING ####

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# N400 mean amplitude by group and priming (collapsed across ISI, hemisphere, and region) for masked picture data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data (collapsed across ISI, hemisphere, and region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")


#### GROUP x PRIMING x ISI ####

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for masked picture data
maskedpic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Picture Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for masked word data
maskedword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Word Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for visible picture data
vispic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Picture Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)

# N400 mean amplitude by group and priming condition (collapsed across hemisphere and region) for visible picture data
visword_data <- subset(wordcrittarg_data, Prime.Visibility == "visible")
visword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Word Data (collapsed across hemisphere and region)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ ISI)


#### GROUP x PRIMING x REGION ####

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for masked picture data
maskedpic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Picture Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for masked word data
maskedword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Masked Word Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for visible picture data
vispic_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Picture Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 ffacet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

# N400 mean amplitude by group and priming  and region (collapsed across hemisphere and ISI) for visible picture data
visword_data %>%
 ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
 stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
 stat_summary(geom="line",fun.data = mean_cl_boot)+
 ggtitle("Visible Word Data (collapsed across hemisphere and ISI)")+
 ylab("Mean Amplitude") +
 xlab("Priming Condition") +
 facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")))

#### GROUP x PRIMING x ISI x HEMISPHERE ####

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
 facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
 facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere (collapsed across region) for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data (collapsed across region)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
 facet_wrap(~ factor(Hemisphere, c("left","midline","right")) + ISI)


#### GROUP x PRIMING x ISI x REGION ####

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

#### GROUP x PRIMING x ISI x HEMISPHERE x REGION ####

# N400 mean amplitude by group and priming condition and hemisphere and region for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)



maskedword_data <- subset(wordcrittarg_data, Prime.Visibility == "masked")
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=interaction(ISI, Group),  color=Group, shape=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") #+
  #facet_wrap(~Group)


visword_data <- subset(wordcrittarg_data, Prime.Visibility == "visible")
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp,  group=interaction(ISI, Group), color=Group, shape=ISI)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") #+
  #facet_wrap(~Group)

#############################
word_fewn400chans_data %>%
  ggplot(aes(x=ISI, y=Mean.Amp, group=Prime.Visibility, color=Prime.Visibility)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("ISI")

pic_fewn400chans_data %>%
  ggplot(aes(x=ISI, y=Mean.Amp, group=Prime.Visibility, color=Prime.Visibility)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("ISI")

```

## Analyses
#### Word Data
Significant predictors: 
  - priming (p < .001)
  - ISI (p < .001)
  - prime visibility x ISI (p < .001) -> licenses separate analyses of data in each of the 4 different visibility x ISI permutations
```{r}
# word_omnibus_red<- lmer(Mean.Amp ~ 1 + Prime.Visibility * Priming * ISI + (1|Participant.ID) + (1|Channel),word_fewn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# word_omnibus_aug <- lmer(Mean.Amp ~ 1 + Prime.Visibility * Priming * ISI + (1+Prime.Visibility*Priming*ISI|Participant.ID) + (1+Prime.Visibility|Channel),word_fewn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# #summary(rePCA(word_omnibus_aug))
# 
# anova(word_omnibus_aug1,word_omnibus_aug)

contrasts(word_fewn400chans_data$Prime.Visibility)<-contr.sum(levels(word_fewn400chans_data$Prime.Visibility))/2
contrasts(word_fewn400chans_data$Priming)<-contr.sum(levels(word_fewn400chans_data$Priming))/2
contrasts(word_fewn400chans_data$ISI)<-contr.sum(levels(word_fewn400chans_data$ISI))/2
word_omnibus<- lmer(Mean.Amp ~ 1 + Prime.Visibility * Priming * ISI + (1|Participant.ID) + (1|Channel),word_fewn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(word_omnibus, show.se = TRUE,show.ci = FALSE)
```

##### Picture Data
Significant predictors:
  - prime visibility (p < .001)
  - ISI (p < .001)
  - prime visibility x ISI (p < .001) -> licenses separate analyses of data in each of the 4 different visibility x ISI permutations
```{r}
# pic_omnibus_red <- lmer(Mean.Amp ~ 1 + Prime.Visibility * Priming * ISI + (1|Participant.ID) + (1|Channel),pic_fewn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# pic_omnibus_aug <- lmer(Mean.Amp ~ 1 + Prime.Visibility * Priming * ISI + (1+Prime.Visibility* Priming* ISI|Participant.ID) + (1+ISI|Channel),pic_fewn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# summary(rePCA(pic_omnibus_aug))
# 
# anova(pic_omnibus_red,pic_omnibus_aug)

contrasts(pic_fewn400chans_data$Prime.Visibility)<-contr.sum(levels(pic_fewn400chans_data$Prime.Visibility))/2
contrasts(pic_fewn400chans_data$Priming)<-contr.sum(levels(pic_fewn400chans_data$Priming))/2
contrasts(pic_fewn400chans_data$ISI)<-contr.sum(levels(pic_fewn400chans_data$ISI))/2
pic_omnibus <- lmer(Mean.Amp ~ 1 + Prime.Visibility * Priming * ISI + (1|Participant.ID) + (1|Channel),pic_fewn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(pic_omnibus, show.se = TRUE,show.ci = FALSE)
```


# Many N400 Channels Data (to examine priming x ISI x group effects at each prime visibility)
## Data Manipulations
```{r}
# Data from many electrodes to measure N400 more comprehensively
# Load data
manyn400chans_data <- read.csv(here("PADLD Data", "Analysis Data","All PADLD Critical Target Mean Amps (50ms pre post bl many electrodes).csv"),stringsAsFactors=TRUE) # mean amplitudes from 30 electrodes at 300 to 500ms post-target onset for all critical targets (with a +/- 50 ms baseline)

# Format data
manyn400chans_data %<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Participant.ID = factor(Participant.ID),
         Channel = factor(Channel),
         Priming=factor(Priming, levels=c("unprimed","primed")),
         ISI = factor(ISI,levels=c("67","317")),
         Experimental.Condition = factor(Experimental.Condition),
         Stimulus.Type = factor(Stimulus.Type),
         Prime.Visibility = factor (Prime.Visibility),
         Trial.Type = factor(Trial.Type),
         Group = factor(Group,levels=c("TL","DLD")))
manyn400chans_data <- subset(manyn400chans_data, Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
#manyn400chans_data <- subset(manyn400chans_data, Participant.ID == '112423-AD-PADLD' | Participant.ID == '041524-JH-PADLD' | Participant.ID == '122923-AS-PADLD' | Participant.ID == '013024-TR-PADLD' | Participant.ID == '032424-JV-PADLD' | Participant.ID == '042524-DH-PADLD' | Participant.ID == '040824-LH-PADLD' | Participant.ID == '010224-BS-PADLD' | Participant.ID == '040924-EK-PADLD' | Participant.ID == '032824-SG-PADLD' | Participant.ID == '101923-DV-PADLD' | Participant.ID == '050624-AF-PADLD' | Participant.ID == '032824-JG-PADLD' | Participant.ID == '013024-LK-PADLD' | Participant.ID == '110123-CB-PADLD' | Participant.ID == '122923-JM-PADLD' | Participant.ID == '040124-CP-PADLD' | Participant.ID == '050924-EL-PADLD')
str(manyn400chans_data )

# Create some data subsets
pic_masked_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "picture" & Prime.Visibility == "masked" & !grepl("^P", Channel) & Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
word_masked_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "word" & Prime.Visibility == "masked" &  !grepl("^FC", Channel) & Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
pic_vis_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "picture" & Prime.Visibility == "visible" & !grepl("^P", Channel) & Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
word_vis_manyn400chans_data <- subset(manyn400chans_data,Experimental.Condition == "word" & Prime.Visibility == "visible" &  !grepl("^FC", Channel)& Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')

# Notes:
# Priming = primed vs. unprimed; default reference level (set above) = unprimed
# ISI = 67 vs. 317; default reference level (set above) = 67
# Experimental Condition = picture vs. word; default reference level = picture
# Stimulus Type = prime vs. target; default reference level = prime (when present)
# Prime Visibility = masked vs. visible; default reference level = masked
# Trial Type = critical vs. probe; default reference level = critical
# Group = DLD vs. TL; default reference level = DLD
```

## Descriptives
```{r}
# N400 mean amplitudes by group, priming condition, experimental condition, and prime visibility (collapsed across region and hemisphere)
manyn400chans_data_grouped1 <- group_by(manyn400chans_data, Experimental.Condition, Prime.Visibility, Group, ISI, Priming)
summarise(manyn400chans_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

manyn400chans_data_grouped1 <- group_by(manyn400chans_data, Experimental.Condition, Prime.Visibility, Group, Priming, ISI)
summarise(manyn400chans_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )


manyn400chans_data_grouped3 <- group_by(manyn400chans_data, Experimental.Condition, Group, Priming)
summarise(manyn400chans_data_grouped3, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

manyn400chans_data_grouped4 <- group_by(manyn400chans_data, Experimental.Condition, Group, ISI)
summarise(manyn400chans_data_grouped4, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

manyn400chans_data_grouped5 <- group_by(manyn400chans_data, Experimental.Condition, Prime.Visibility, Group, ISI)
summarise(manyn400chans_data_grouped5, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

```

## Visualizations
```{r}
word_masked_manyn400chans_data %>%
  ggplot(aes(x=ISI, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("ISI")

pic_masked_manyn400chans_data %>%
  ggplot(aes(x=ISI, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("ISI")


```

## Analyses
### Word Data
#### Masked Word Data
Results:
  - Priming (p < .001)
  - ISI (p < .001)
  - Priming x Group (p = .050)
  - ISI x Group (p < .001)
  - Priming x ISI x Group (p = .180 (ns))
    - priming effects for TD kids at both ISIs (both ps < .001) but no priming effects for kids with DLD (both ps > .16)
```{r}
# word_masked_manychans_red <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),word_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# word_masked_manychans_aug <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1+Priming*ISI|Participant.ID) + (1+ISI|Channel),word_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# anova(word_masked_manychans_red,word_masked_manychans_aug)

contrasts(word_masked_manyn400chans_data$Group)<-contr.sum(levels(word_masked_manyn400chans_data$Group))/2
contrasts(word_masked_manyn400chans_data$Priming)<-contr.sum(levels(word_masked_manyn400chans_data$Priming))/2
contrasts(word_masked_manyn400chans_data$ISI)<-contr.sum(levels(word_masked_manyn400chans_data$ISI))/2
word_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),word_masked_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(word_masked_manychans, show.se = TRUE,show.ci = FALSE)

word_masked_emm <- emmeans(word_masked_manychans, pairwise ~ Priming | ISI*Group, adjust = "none")
word_masked_emm
tidy(pairs(word_masked_emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))
```

#### Visible Word Data
Results:
  - Priming (p < .001)
  - ISI (p = .014)
  - ISI x Group (p < .001)
  - Priming x ISI x Group (p = .419 (ns))
    - priming effects for TD kids and kids with DLD at both ISIs (all ps < .002)
```{r}
# word_vis_manychans_red <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),word_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# word_vis_manychans_aug <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1+Priming*ISI|Participant.ID) + (1+Group|Channel),word_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# anova(word_vis_manychans_red,word_vis_manychans_aug)

contrasts(word_vis_manyn400chans_data$Group)<-contr.sum(levels(word_vis_manyn400chans_data$Group))/2
contrasts(word_vis_manyn400chans_data$Priming)<-contr.sum(levels(word_vis_manyn400chans_data$Priming))/2
contrasts(word_vis_manyn400chans_data$ISI)<-contr.sum(levels(word_vis_manyn400chans_data$ISI))/2
word_vis_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),word_vis_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(word_vis_manychans, show.se = TRUE,show.ci = FALSE)

word_vis_emm <- emmeans(word_vis_manychans, pairwise ~ Priming | ISI*Group, adjust = "none")
word_vis_emm
tidy(pairs(word_vis_emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))
```

### Picture Data
#### Masked Picture Data
Results:
  - Priming (p < .001)
  - ISI (p < .001)
  - ISI x Group (p < .001)
  - Priming x ISI x Group (p = .066 (ns))
    - priming effects at both ISIs for TD kids (both ps < .001) and priming effects at the shorter ISI for kids with DLD (p = .003) (not the longer ISI though; p = 0.178)
```{r}
# pic_masked_manychans_red <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),pic_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# pic_masked_manychans_aug <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1+Priming*ISI+Group|Participant.ID) + (1|Channel),pic_masked_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# anova(pic_masked_manychans_red,pic_masked_manychans_aug)

contrasts(pic_masked_manyn400chans_data$Group)<-contr.sum(levels(pic_masked_manyn400chans_data$Group))/2
contrasts(pic_masked_manyn400chans_data$Priming)<-contr.sum(levels(pic_masked_manyn400chans_data$Priming))/2
contrasts(pic_masked_manyn400chans_data$ISI)<-contr.sum(levels(pic_masked_manyn400chans_data$ISI))/2
pic_masked_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),pic_masked_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(pic_masked_manychans, show.se = TRUE,show.ci = FALSE)

pic_masked_emm <- emmeans(pic_masked_manychans, pairwise ~ Priming | ISI*Group, adjust = "none")
pic_masked_emm
tidy(pairs(pic_masked_emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))

```

#### Visible Picture Data
Results:
  - Priming (p < .001)
  - ISI (p < .001)
  - ISI x Group (p < .001)
  - Priming x ISI x Group (p = .528 (ns))
    - priming effects for TD kids and kids with DLD at both ISIs (all ps < .001)
```{r}
# pic_vis_manychans_red <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),pic_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# pic_vis_manychans_aug <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1+Priming*ISI|Participant.ID) + (1+Priming|Channel),pic_vis_manyn400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# 
# anova(pic_vis_manychans_red,pic_vis_manychans_aug)

contrasts(pic_vis_manyn400chans_data$Group)<-contr.sum(levels(pic_vis_manyn400chans_data$Group))/2
contrasts(pic_vis_manyn400chans_data$Priming)<-contr.sum(levels(pic_vis_manyn400chans_data$Priming))/2
contrasts(pic_vis_manyn400chans_data$ISI)<-contr.sum(levels(pic_vis_manyn400chans_data$ISI))/2
pic_vis_manychans <- lmer(Mean.Amp ~ 1 + Priming * ISI * Group + (1|Participant.ID) + (1|Channel),pic_vis_manyn400chans_data, REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(pic_vis_manychans, show.se = TRUE,show.ci = FALSE)

pic_vis_emm <- emmeans(pic_vis_manychans, pairwise ~ Priming | ISI*Group, adjust = "none")
pic_vis_emm
tidy(pairs(pic_vis_emm, adjust="none"))%>%
      mutate(signif = stars.pval(p.value), p.value = formatC(p.value, format = "f", digits = 4))
```

# Difference Score Data (to examine link btw the time course of ASA and semantic abilities)
## Data Manipulations
```{r}
# Load data (2 data frames)
diffscore_data <- read.csv(here("PADLD Data", "Analysis Data","PADLD Difference Score Data (many electrodes).csv"),stringsAsFactors=TRUE) # N400 priming effect difference scores (67 ms ISI diff wave - 317 ms ISI diff wave) from 30 individual electrodes
clusterdiffscore_data <- read.csv(here("PADLD Data", "Analysis Data","PADLD Difference Score Data (cluster electrode).csv"),stringsAsFactors=TRUE) # N400 priming effect difference scores (67 ms ISI diff wave - 317 ms ISI diff wave) from the average of the 30 individual electrodes

# Format data
diffscore_data %<>%
  mutate(PrimingxISI.Diff = as.numeric(PrimingxISI.Diff),
         Participant.ID = factor(Participant.ID),
         Channel = factor(Channel),
         Prime.Visibility = factor(Prime.Visibility),
         Experimental.Condition = factor(Experimental.Condition),
         tills = as.numeric(TILLS),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         tills.c.z = as.numeric(scale(tills, scale = TRUE, center = TRUE)),
         tills.c = as.numeric(scale(tills, scale = FALSE, center = TRUE)),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)))
str(diffscore_data)

clusterdiffscore_data %<>%
  mutate(PrimingxISI.Diff = as.numeric(PrimingxISI.Diff),
         Participant.ID = factor(Participant.ID),
         Prime.Visibility = factor(Prime.Visibility),
         Experimental.Condition = factor(Experimental.Condition),
         tills = as.numeric(TILLS),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         tills.c.z = as.numeric(scale(tills, scale = TRUE, center = TRUE)),
         tills.c = as.numeric(scale(tills, scale = FALSE, center = TRUE)),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age = as.numeric(Average.Age),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)),
         pvt.z = as.numeric(scale(PVT.Numeric, scale = TRUE)))
str(clusterdiffscore_data)

# Create some data subsets
#diffscore_data <- subset(diffscore_data, Participant.ID == '112423-AD-PADLD' | Participant.ID == '041524-JH-PADLD' | Participant.ID == '122923-AS-PADLD' | Participant.ID == '013024-TR-PADLD' | Participant.ID == '032424-JV-PADLD' | Participant.ID == '042524-DH-PADLD' | Participant.ID == '040824-LH-PADLD' | Participant.ID == '010224-BS-PADLD' | Participant.ID == '040924-EK-PADLD' | Participant.ID == '032824-SG-PADLD' | Participant.ID == '101923-DV-PADLD' | Participant.ID == '050624-AF-PADLD' | Participant.ID == '032824-JG-PADLD' | Participant.ID == '013024-LK-PADLD' | Participant.ID == '110123-CB-PADLD' | Participant.ID == '122923-JM-PADLD' | Participant.ID == '040124-CP-PADLD' | Participant.ID == '050924-EL-PADLD')
#clusterdiffscore_data<- subset(clusterdiffscore_data, Participant.ID == '112423-AD-PADLD' | Participant.ID == '041524-JH-PADLD' | Participant.ID == '122923-AS-PADLD' | Participant.ID == '013024-TR-PADLD' | Participant.ID == '032424-JV-PADLD' | Participant.ID == '042524-DH-PADLD' | Participant.ID == '040824-LH-PADLD' | Participant.ID == '010224-BS-PADLD' | Participant.ID == '040924-EK-PADLD' | Participant.ID == '032824-SG-PADLD' | Participant.ID == '101923-DV-PADLD' | Participant.ID == '050624-AF-PADLD' | Participant.ID == '032824-JG-PADLD' | Participant.ID == '013024-LK-PADLD' | Participant.ID == '110123-CB-PADLD' | Participant.ID == '122923-JM-PADLD' | Participant.ID == '040124-CP-PADLD' | Participant.ID == '050924-EL-PADLD')

masked_diffscores_data <- subset(diffscore_data, Prime.Visibility == "masked")
vis_diffscores_data <- subset(diffscore_data, Prime.Visibility == "visible")

pic_masked_diffscores_data <- subset(diffscore_data,Experimental.Condition == "picture" & Prime.Visibility == "masked" & !grepl("^P", Channel)& Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
word_masked_diffscores_data <- subset(diffscore_data,Experimental.Condition == "word" & Prime.Visibility == "masked" & !grepl("^FC", Channel)& Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
pic_vis_diffscores_data <- subset(diffscore_data,Experimental.Condition == "picture" & Prime.Visibility == "visible" & !grepl("^P", Channel)& Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')
word_vis_diffscores_data <- subset(diffscore_data,Experimental.Condition == "word" & Prime.Visibility == "visible" & !grepl("^FC", Channel)& Channel != 'F1'&Channel !='F2'&Channel !='F3'&Channel !='F4'&Channel !='FZ'&Channel !='F6')

masked_clusterdiffscores_data <- subset(clusterdiffscore_data, Prime.Visibility == "masked")
vis_clusterdiffscores_data <- subset(clusterdiffscore_data, Prime.Visibility == "visible")

pic_masked_clusterdiffscores_data <- subset(clusterdiffscore_data,Experimental.Condition == "picture" & Prime.Visibility == "masked")
word_masked_clusterdiffscores_data <- subset(clusterdiffscore_data,Experimental.Condition == "word" & Prime.Visibility == "masked")
pic_vis_clusterdiffscores_data <- subset(clusterdiffscore_data,Experimental.Condition == "picture" & Prime.Visibility == "visible")
word_vis_clusterdiffscores_data <- subset(clusterdiffscore_data,Experimental.Condition == "word" & Prime.Visibility == "visible")

# Notes:
# Experimental Condition = picture vs. word; default reference level = picture
# Prime Visibility = masked vs. visible; default reference level = masked
```

## Analyses
### Masked Data
Significant results:
  - when using a cluster electrode, nothing - neither masked word nor masked picture ISI differences significantly predict or are correlated with TILLS VA scores (nor vice versa) 
  - when using individual electrodes and difference scores as the DV and put all the data in one model, significant TILLS x experimental condition interaction
      - as TILLS scores increase, priming difference increases for word data and decreases for picture data
```{r}
# Word and Picture

# masked_diffscores <- lmer(tills.z ~ 1 + PrimingxISI.Diff*Experimental.Condition +(1|Participant.ID), diffscore_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # failed to converge

masked_clusterdiffscores <- lm(tills.z ~ 1 + PrimingxISI.Diff*Experimental.Condition, masked_clusterdiffscores_data)
tab_model(masked_clusterdiffscores)

masked_diffscore <- lmer(PrimingxISI.Diff ~ 1 + tills.c.z*Experimental.Condition +(1|Participant.ID), masked_diffscores_data, REML = TRUE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(masked_diffscore, show.se = TRUE,show.ci = FALSE)

masked_diffscores_data %>%
  ggplot(aes(x=tills.c.z, y=PrimingxISI.Diff, group=Experimental.Condition, color=Experimental.Condition, shape=Experimental.Condition)) +
  geom_point()+
  # stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  # stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Difference Scores")+
  ylab("Priming x ISI Difference Score") +
  xlab("TILLS z-score")+
  geom_smooth(method=lm)

# Word
#word_masked_diffscores <- lmer(tills.z ~ 1 + PrimingxISI.Diff +(1|Participant.ID), word_masked_diffscores_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # failed to converge

word_masked_clusterdiffscores <- lm(tills.z ~ 1 + PrimingxISI.Diff, word_masked_clusterdiffscores_data)
tab_model(word_masked_clusterdiffscores, show.se = TRUE,show.ci = FALSE)

word_masked_clusterdiffscores.null <- lm(tills.z ~ 1, word_masked_clusterdiffscores_data)
anova(word_masked_clusterdiffscores,word_masked_clusterdiffscores.null)

word_masked_diffscores <- lmer(PrimingxISI.Diff ~ 1 + tills.z +(1|Participant.ID), word_masked_diffscores_data, REML = TRUE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) 
tab_model(word_masked_diffscores)

# Correlations
word_masked_corr <- cor.test(word_masked_clusterdiffscores_data$PrimingxISI.Diff, word_masked_clusterdiffscores_data$tills.z, 
                    method = "pearson")
tidy(word_masked_corr)

# Compute a correlation matrix of the data rounding to 2 decimal places
library(ggcorrplot)
word_masked_covar_corr_data <- subset(word_masked_clusterdiffscores_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','PrimingxISI.Diff'))
word_masked_covar_corr <- round(cor(word_masked_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(word_masked_covar_corr)

ggcorrplot(
  word_masked_covar_corr,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

word_masked_covar_corr
p.mat

# Picture
# pic_masked_diffscores_red <- lmer(tills.z ~ 1 + PrimingxISI.Diff +(1|Participant.ID), pic_masked_diffscores_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # failed to converge

pic_masked_clusterdiffscores <- lm(tills.z ~ 1 + PrimingxISI.Diff, pic_masked_clusterdiffscores_data)
tab_model(pic_masked_clusterdiffscores, show.se = TRUE,show.ci = FALSE)

pic_masked_clusterdiffscores.null <- lm(tills.z ~ 1, pic_masked_clusterdiffscores_data)
anova(pic_masked_clusterdiffscores,pic_masked_clusterdiffscores.null)

pic_masked_diffscores <- lmer(PrimingxISI.Diff ~ 1 + tills.c.z +(1|Participant.ID), pic_masked_diffscores_data, REML = TRUE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(pic_masked_diffscores)

# Correlations
pic_masked_corr <- cor.test(pic_masked_clusterdiffscores_data$PrimingxISI.Diff, pic_masked_clusterdiffscores_data$tills.z, 
                    method = "pearson")
tidy(pic_masked_corr)

# Compute a correlation matrix of the data rounding to 2 decimal places
library(ggcorrplot)
pic_masked_clusterdiffscores_data <- subset(pic_masked_clusterdiffscores_data, Participant.ID != "050724-AF-PADLD")
pic_masked_covar_corr_data <- subset(pic_masked_clusterdiffscores_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','PrimingxISI.Diff'))
pic_masked_covar_corr <- round(cor(pic_masked_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(pic_masked_covar_corr)

ggcorrplot(
  pic_masked_covar_corr,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

pic_masked_covar_corr
p.mat

pic_masked_clusterdiffscores_data %>%
  ggplot(aes(x=celf5, y=PrimingxISI.Diff))+#, group=Experimental.Condition, color=Experimental.Condition, shape=Experimental.Condition)) +
  geom_point()+
  # stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  # stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Difference Scores")+
  ylab("Priming x ISI Difference Score") +
  xlab("CELF-5")+
  geom_smooth(method=lm)

```

### Visible Data
Significant results:
  - when using a cluster electrode, nothing - neither visible word nor visible picture ISI differences significantly predict or are correlated with TILLS VA scores (nor vice versa)
    - when using individual electrodes and difference scores as the DV and put all the data in one model, significant TILLS x experimental condition interaction
      - as TILLS scores increase, priming difference increases for picture data and decreases for word data (reverse of masked data finding)
```{r}
# Word and Picture
vis_diffscores <- lmer(tills.z ~ 1 + PrimingxISI.Diff*Experimental.Condition +(1|Participant.ID), diffscore_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # failed to converge

vis_clusterdiffscores <- lm(tills.z ~ 1 + PrimingxISI.Diff*Experimental.Condition, vis_clusterdiffscores_data)
tab_model(vis_clusterdiffscores)

vis_diffscore <- lmer(PrimingxISI.Diff ~ 1 + tills.c.z*Experimental.Condition +(1|Participant.ID), vis_diffscores_data, REML = TRUE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(vis_diffscore)

vis_diffscores_data %>%
  ggplot(aes(x=tills, y=PrimingxISI.Diff, group=Experimental.Condition, color=Experimental.Condition, shape=Experimental.Condition)) +
  geom_point()+
  # stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  # stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Difference Scores")+
  ylab("Priming x ISI Difference Score") +
  xlab("TILLS z-score")+
  geom_smooth(method=lm)


# Word
word_vis_diffscores <- lmer(tills.z ~ 1 + PrimingxISI.Diff +(1|Participant.ID), word_vis_diffscores_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # failed to converge

word_vis_clusterdiffscores <- lm(tills.z ~ 1 + PrimingxISI.Diff, word_vis_clusterdiffscores_data)
tab_model(word_vis_clusterdiffscores)

word_vis_diffscores <- lmer(PrimingxISI.Diff ~ 1 + tills.c.z +(1|Participant.ID), word_vis_diffscores_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) 
tab_model(word_vis_diffscores)

# Correlations
word_vis_corr <- cor.test(word_vis_clusterdiffscores_data$PrimingxISI.Diff, word_vis_clusterdiffscores_data$tills.z, 
                    method = "pearson")
tidy(word_vis_corr)

# Picture
pic_vis_diffscores_red <- lmer(tills.z ~ 1 + PrimingxISI.Diff +(1|Participant.ID), pic_vis_diffscores_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # failed to converge

pic_vis_clusterdiffscores <- lm(tills.z ~ 1 + PrimingxISI.Diff, pic_vis_clusterdiffscores_data)
tab_model(pic_vis_clusterdiffscores)

pic_vis_diffscores <- lmer(PrimingxISI.Diff ~ 1 + tills.c.z +(1|Participant.ID), pic_vis_diffscores_data, REML = FALSE, control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) 
tab_model(pic_vis_diffscores)

# Correlations
pic_vis_corr <- cor.test(pic_vis_clusterdiffscores_data$PrimingxISI.Diff, pic_vis_clusterdiffscores_data$tills.z, 
                    method = "pearson")
tidy(pic_vis_corr)
```


# Difference Waves Data (to examine covariates/indiviudal differences)
## Data Manipulations
```{r}
# Load data (3 data frames)
diffwaves_data <- read.csv(here("PADLD Data", "Analysis Data","All PADLD Critical Target Mean Amps (50ms pre post bl many electrodes diff waves).csv"), stringsAsFactors=TRUE) # mean amplitudes of unprimed - primed ERPs from 30 individual electrodes (including the traditional ones) at 300 to 500ms post-target onset for all critical targets (with a +/- 50 ms baseline)

clusterdiffwaves_data <- read.csv(here("PADLD Data", "Analysis Data","PADLD Difference Waves Data (cluster electrode).csv"), stringsAsFactors=TRUE) # mean amplitudes of unprimed - primed ERPs from the average of the 30 individual electrodes

covar_data <- read.csv(here("PADLD Data", "Participant Information","Participant Information & Scores v080824.csv"),stringsAsFactors=TRUE) # behavioral assessment measures

# Format data
diffwaves_data%<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Participant.ID = factor(Participant.ID),
         Channel = factor(Channel),
         ISI = factor(ISI,levels=c("67","317")),
         Experimental.Condition = factor(Experimental.Condition),
         Prime.Visibility = factor (Prime.Visibility),
         Group = factor(Group),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z.c = as.numeric(scale(celf5, scale = TRUE, center = TRUE)),
         age = as.numeric(Average.Age),
         age.z.c = as.numeric(scale(age, scale = TRUE, center = TRUE)),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z.c = as.numeric(scale(nwrppc.arc, scale = TRUE, center = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z.c = as.numeric(scale(nwrpcc.arc, scale = TRUE, center = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z.c = as.numeric(scale(tills, scale = TRUE, center = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z.c = as.numeric(scale(toni, scale = TRUE, center = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z.c = as.numeric(scale(wrmt, scale = TRUE, center = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z.c = as.numeric(scale(flanker, scale = TRUE, center = TRUE)),
         gender.c = as.numeric(Gender) - 1.5,
         Detailed.Language.Status = factor(Detailed.Language.Status),
         Language.Status = factor(Language.Status,levels=c("English monolingual","English primary")),
         langstat.c = as.numeric(Language.Status) - 1.5,
         Bilingual.Type = factor(Bilingual.Type),
         handedness = factor(Handedness),
         hand.c = as.numeric(handedness) - 1.5,
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")),
         pvt.z.c = as.numeric(scale(PVT.Numeric, scale = TRUE, center = TRUE)),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)),
         pvt.z = as.numeric(scale(PVT.Numeric, scale = TRUE)))
str(diffwaves_data)

clusterdiffwaves_data%<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Participant.ID = factor(Participant.ID),
         ISI = factor(ISI,levels=c("67","317")),
         Experimental.Condition = factor(Experimental.Condition),
         Prime.Visibility = factor (Prime.Visibility),
         Group = factor(Group),
         celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z.c = as.numeric(scale(celf5, scale = TRUE, center = TRUE)),
         age = as.numeric(Average.Age),
         age.z.c = as.numeric(scale(age, scale = TRUE, center = TRUE)),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z.c = as.numeric(scale(nwrppc.arc, scale = TRUE, center = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z.c = as.numeric(scale(nwrpcc.arc, scale = TRUE, center = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z.c = as.numeric(scale(tills, scale = TRUE, center = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z.c = as.numeric(scale(toni, scale = TRUE, center = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z.c = as.numeric(scale(wrmt, scale = TRUE, center = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z.c = as.numeric(scale(flanker, scale = TRUE, center = TRUE)),
         gender.c = as.numeric(Gender) - 1.5,
         Detailed.Language.Status = factor(Detailed.Language.Status),
         Language.Status = factor(Language.Status,levels=c("English monolingual","English primary")),
         langstat.c = as.numeric(Language.Status) - 1.5,
         Bilingual.Type = factor(Bilingual.Type),
         handedness = factor(Handedness),
         hand.c = as.numeric(handedness) - 1.5,
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")),
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")),
         pvt.z.c = as.numeric(scale(PVT.Numeric, scale = TRUE, center = TRUE)),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)),
         pvt.z = as.numeric(scale(PVT.Numeric, scale = TRUE)))
str(clusterdiffwaves_data)

# z-score values
covar_data %<>%
  mutate(celf5 = as.numeric(CELF.5.Core.Language.Score),
         celf5.z = as.numeric(scale(celf5, scale = TRUE)),
         age = as.numeric(Average.Age),
         age.z = as.numeric(scale(age, scale = TRUE)),
         nwrppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwrppc.arc.z = as.numeric(scale(nwrppc.arc, scale = TRUE)),
         nwrpcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwrpcc.arc.z = as.numeric(scale(nwrpcc.arc, scale = TRUE)),
         tills = as.numeric(TILLS.VA.Standard.Score),
         tills.z = as.numeric(scale(tills, scale = TRUE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.z = as.numeric(scale(toni, scale = TRUE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.z = as.numeric(scale(wrmt, scale = TRUE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.z = as.numeric(scale(flanker, scale = TRUE)))
str(covar_data)

# Notes:
# ISI = 67 vs. 317; default reference level (set above) = 67
# Experimental Condition = picture vs. word; default reference level = picture
# Prime Visibility = masked vs. visible; default reference level = masked
# Group = DLD vs. TL; default reference level = DLD
# For gender, female = -0.5 (after centering), male = 0.5 (after centering)
# Detailed Language Status = language status + bilingual type (see below); default reference level= English monolingual
# Language Status = English monolingual vs. English primary; default reference level (set above) \ = English monolingual
# For language status, English monolingual = -0.5 (after centering), English primary/bilingual = 0.5 (after centering)
# Bilingual Type = sequential vs. simultaneous and the languages spoken; default reference level = NA? sequential bilingual (English-French)?
# For handedness, L = -0.5 (after centering), R = 0.5 (after centering)
# PVT = prime visibility threshold (shortest prime duration at which participant identified > 50% of animal primes presented at that duration); 50 vs. 67 vs. 83 vs. 100 vs. 117 vs. > 117; default reference level (set above) = 50
# PVT Numeric = > 117 is replaced with 150 to make the variable closer to continuous rather than catergorical
```

## Analyses
### Correlations
Results: 
  - nothing is significantly or even strongly correlated except for NWR PPC and NWR PCC (to be expected since they are measures from the same test)
```{r}
# Compute a correlation matrix of the data rounding to 2 decimal places
library(ggcorrplot)
covar_corr_data <- subset(covar_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z'))
#covar_corr_data <- subset(covar_data, select = c('celf5', 'nwrppc.arc', 'nwrpcc.arc', 'tills', 'toni', 'wrmt', 'flanker', 'age'))
corr <- round(cor(covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(covar_corr_data)

ggcorrplot(
  corr,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

```

### Word Data
Significant results (when using non-clustered electrodes as DV, i.e., lmer):
 - CELF-5 predicts priming effects for targets following visible primes and a 317-ms ISI (p = .035)
Significant results (when using cluster electrode as DV, i.e., lm):
  - nothing
```{r}
# Create some data subsets
word_masked_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "67")
word_masked_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "317")
word_vis_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "67")
word_vis_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "317")

word_masked_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "67")
word_masked_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Masked" & ISI == "317")
word_vis_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "67")
word_vis_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "word" & Prime.Visibility == "Visible" & ISI == "317")

# Run some regressions
word_masked_67_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID) + (1|Channel), word_masked_67_diffwaves_data) 
tab_model(word_masked_67_covartest)

word_masked_317_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c+ (1|Participant.ID), word_masked_317_diffwaves_data) 
tab_model(word_masked_317_covartest)

word_vis_67_covartest<- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID) + (1|Channel), word_vis_67_diffwaves_data) 
tab_model(word_vis_67_covartest)

word_vis_317_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID), word_vis_317_diffwaves_data) 
tab_model(word_vis_317_covartest)

# Compute a correlation matrix of the data rounding to 2 decimal places
word_masked_67_covar_corr_data <- subset(word_masked_67_clusterdiffwaves_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','Mean.Amp'))
word_masked_67_covar_cor <- round(cor(word_masked_67_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(word_masked_67_covar_corr_data)

ggcorrplot(
  word_masked_67_covar_cor,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

# Compute a correlation matrix of the data rounding to 2 decimal places
word_masked_317_covar_corr_data <- subset(word_masked_317_clusterdiffwaves_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','Mean.Amp'))
word_masked_317_covar_corr <- round(cor(word_masked_317_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(word_masked_317_covar_corr_data)

ggcorrplot(
  word_masked_317_covar_corr,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

```

### Picture Data
Significant results (when using non-clustered electrodes as DV, i.e., lmer):
 - Gender and participants' prime visibility threshold predicts priming effects for targets following visible primes and a 317-ms ISI (ps = .038 and .046, respectively)
Significant results (when using cluster electrode as DV, i.e., lm):
  - participants' prime visibility threshold predicts priming effects for targets following visible primes and a 317-ms ISI (p = .019)
```{r}
# Create some data subsets
pic_masked_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "67")
pic_masked_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "317")
pic_vis_67_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "67")
pic_vis_317_diffwaves_data <- subset(diffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "317")

pic_masked_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "67")
pic_masked_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Masked" & ISI == "317")
pic_vis_67_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "67")
pic_vis_317_clusterdiffwaves_data <- subset(clusterdiffwaves_data,Experimental.Condition == "picture" & Prime.Visibility == "Visible" & ISI == "317")


# Run some regressions
pic_masked_67_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID) + (1|Channel), pic_masked_67_diffwaves_data) 
tab_model(pic_masked_67_covartest)

pic_masked_317_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c+ (1|Participant.ID) + (1|Channel), pic_masked_317_diffwaves_data) 
tab_model(pic_masked_317_covartest)

pic_vis_67_covartest<- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID) + (1|Channel), pic_vis_67_diffwaves_data) 
tab_model(pic_vis_67_covartest)

pic_vis_317_covartest <- lmer(Mean.Amp ~ 1 + celf5.z.c + age.z.c + nwrppc.arc.z.c + tills.z.c + toni.z.c + wrmt.z.c + flanker.z.c + gender.c + hand.c + langstat.c + pvt.z.c + (1|Participant.ID), pic_vis_317_diffwaves_data) 
tab_model(pic_vis_317_covartest)


# Compute a correlation matrix of the data rounding to 2 decimal places
pic_masked_67_covar_corr_data <- subset(pic_masked_67_clusterdiffwaves_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','Mean.Amp'))
pic_masked_67_covar_cor <- round(cor(pic_masked_67_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(pic_masked_67_covar_corr_data)

ggcorrplot(
  pic_masked_67_covar_cor,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

# Compute a correlation matrix of the data rounding to 2 decimal places
pic_masked_317_covar_corr_data <- subset(pic_masked_317_clusterdiffwaves_data, select = c('celf5.z', 'nwrppc.arc.z', 'nwrpcc.arc.z', 'tills.z', 'toni.z', 'wrmt.z', 'flanker.z', 'age.z','pvt.z','Mean.Amp'))
pic_masked_317_covar_corr <- round(cor(pic_masked_317_covar_corr_data), 2)

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(pic_masked_317_covar_corr_data)

ggcorrplot(
  pic_masked_317_covar_corr,
  method = "circle",
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)

```


