---
title: "PADLD Diff Score Analyses"
author: "Ashlie"
date: "2024-08-01"
output: html_document
---

```{r setup, include=FALSE}

# Libraries
pacman::p_load(knitr, # rendering of .Rmd file
               lme4, # model specification/estimation
               afex, # anova and deriving p-values via LRTs from lmer
               broom.mixed, # extracting data from model fits
               faux, # generate correlated values
               tidyverse, # data wrangling and visualization 
               ggridges, # visualization
               viridis, # color schemes for visualization
               kableExtra, # helps with knitting the .Rmd file
               cowplot, # visualization tool to include multiple plots
               ggrain, # visualization tool for raincloud plots
               dplyr, # data manipulation tools
               here, # controlling directories/reproducibility
               tidyr, # formatting package
               readr, # data importation
               Hmisc, # visualization
               emmeans, # estimation of marginal means and contrasts
               sjstats, # estimation of marginal means and contrasts
               lmerTest, # deriving p-values from lmer
               MuMIn, # ?
               sjPlot, # APA formatting of numerical output
               car, # data wrangling and visualization,
               magrittr, # to use %>%
               ggpubr, # ? (Rose had it in her script)
               broom, # ? (Rose had it in her script)
               Matrix, # model specification/estimation,
               multcomp, # multiple comparison adjustments
               forcats, # organizing visualizations
               gtools, # data manipulation/wrangling
               fuzzySim, # FDR correction,
               ez, # anova
               apaTables, # visualization of anova output
               #renv # package versioning/reproducibility
               )

# Global theme set
set.seed(1234) # set random seed for reproducibility

knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)

#theme_set(theme_bw(base_size = 13) + theme(text = element_text(size=13), 
                             #axis.title=element_text(size=12),
                             #strip.text = element_text(margin=margin(2,0,2,0)), 
                             #panel.grid = element_blank()))

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE, fig.width=10, fig.height=8, fig.fullwidth=TRUE)

plot_theme <- 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18), 
        axis.text.x = element_text(size = 13), 
        axis.title.x = element_text(size = 13), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 13),
        strip.background = element_rect(color="white", fill="white", linewidth = 1.5, linetype="solid"))

options(scipen=0)
```

# All Diff Score Data

## Data Manipulation
```{r}
# Load data (1 data frame)
diffscore_data <- read.csv(here("PADLD Data", "PADLD Diff Scores Data.csv"),stringsAsFactors=TRUE) # N400 priming effect difference scores

diffscore_data %<>%
  mutate(Priming.Diff.Score = as.numeric(Priming.Diff.Score),
         Channel = factor(Channel),
         Region = factor(Region, levels=c("frontal","central","parietal","occipital")),
         Hemisphere = factor(Hemisphere, levels=c("left","midline","right")),
         Experimental.Condition = factor(Experimental.Condition),
         Prime.Visibility = factor (Prime.Visibility),
         Group = factor(Group), 
         gender.c = as.numeric(Gender) - 1.5,
         Detailed.Language.Status = factor(Detailed.Language.Status),
         Language.Status = factor(Language.Status,levels=c("English monolingual","English primary")),
         lang.stat.c = as.numeric(Language.Status) - 1.5,
         Bilingual.Type = factor(Bilingual.Type),
         celf5 = as.numeric(CELF5.CLS),
         celf5.c = as.numeric(scale(CELF5.CLS, center = TRUE, scale = FALSE)),
         age.c = as.numeric(scale(Average.Age, center = TRUE, scale = FALSE)),
         nwr.ppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwr.ppc.arc.c = as.numeric(scale(nwr.ppc.arc, center = TRUE, scale = FALSE)),
         nwr.pcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwr.pcc.arc.c = as.numeric(scale(nwr.pcc.arc, center = TRUE, scale = FALSE)),
         tills= as.numeric(TILLS.VA.Standard.Score),
         tills.c = as.numeric(scale(TILLS.VA.Standard.Score, center = TRUE, scale = FALSE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.c = as.numeric(scale(TONI.Deviation.Quotient, center = TRUE, scale = FALSE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.c = as.numeric(scale(WRMT.LWI.Standard.Score, center = TRUE, scale = FALSE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.c = as.numeric(scale(Flanker.Standard.Score, center = TRUE, scale = FALSE)),
         handedness = factor(Handedness),
         hand.c = as.numeric(handedness) - 1.5,
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")))
str(diffscore_data)

# Create some data subsets
masked_diffscore_data <- subset(diffscore_data, Prime.Visibility == "masked")
vis_diffscore_data <- subset(diffscore_data, Prime.Visibility == "visible")

# Notes:
# Region = anteriority/posteriority; default reference level (set above) = frontal
# Hemisphere = laterality; default reference level (set above) = left
# Experimental Condition = picture vs. word; default reference level = picture
# Prime Visibility = masked vs. visible; default reference level = masked
# Group = DLD vs. TL; default reference level = DLD
# For gender, female = -0.5 (after centering), male = 0.5 (after centering)
# Detailed Language Status = language status + bilingual type (see below); default reference level= English monolingual
# Language Status = English monolingual vs. English primary; default reference level (set above) \ = English monolingual
# For language status, English monolingual = -0.5 (after centering), English primary/bilingual = 0.5 (after centering)
# Bilingual Type = sequential vs. simultaneous and the languages spoken; default reference level = NA? sequential bilingual (English-French)?
# For handedness, L = -0.5 (after centering), R = 0.5 (after centering)
# PVT = prime visibility threshold (shortest prime duration at which participant identified > 50% of animal primes presented at that duration); 50 vs. 67 vs. 83 vs. 100 vs. > 117; default reference level (set above) = 50
```

## Analyses
### Finding the maximal convergent model
#### Masked Data
FINAL BASE MODELS: 
diffscoresmaskedm3 <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere, data=masked_diffscore_data)
diffscoresmaskedm6 <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + (1+Experimental.Condition|Participant.ID) , data=masked_diffscore_data
```{r}
diffscoresmaskedm1 <- lmer(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(diffscoresmaskedm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

diffscoresmaskedm2 <- lmer(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere + (1|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # model failed to converge, so checking random effects' variances
summary(rePCA(diffscoresmaskedm2)) # PCA results an extremely large SD for the random intercept of Participant ID, so trying removing random effects altogether

diffscoresmaskedm3 <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere, data=masked_diffscore_data) # converges! now to test covariates

diffscoresmaskedm4 <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + (1|Participant.ID) + (1|Channel) , data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning and failed to converge, so checking random effects' variances
summary(rePCA(diffscoresmaskedwordm4)) # PCA results indicate close to no variability in the random effects for Channel, so trying a model with that random effect removed

diffscoresmaskedm5 <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + (1|Participant.ID) , data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now to build random effects

diffscoresmaskedm6 <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + (1+tills.c|Participant.ID) , data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning; continuing to build random effects structure

diffscoresmaskedm6 <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + (1+Experimental.Condition|Participant.ID) , data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now to test covariates

```

### Testing impact of covariates
#### Masked Data
##### TILLS as DV
FINAL MODEL:diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c + nwr.ppc.arc.c + toni.c + wrmt.c +  hand.c  +  pvt , data=masked_diffscore_data)
```{r}
diffscoresmaskedm3.gender <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere + gender.c , data=masked_diffscore_data) # to determine whether gender significantly improves model fit
anova(diffscoresmaskedm3,diffscoresmaskedm3.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender over diffscoresmaskedm3

diffscoresmaskedm3.gender.age <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere + gender.c  +age.c , data=masked_diffscore_data) # to determine whether age significantly improves model fit
anova(diffscoresmaskedm3.gender,diffscoresmaskedm3.gender.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model -->significant: prefer diffscoresmaskedm3.gender.age over diffscoresmaskedm3.gender

diffscoresmaskedm3.gender.age.langstat <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere  + gender.c + age.c  + lang.stat.c , data=masked_diffscore_data) # to determine whether language status significantly improves model fit
anova(diffscoresmaskedm3.gender.age, diffscoresmaskedm3.gender.age.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender.age.langstat over diffscoresmaskedm3.gender.age

diffscoresmaskedm3.gender.age.langstat.celf <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere  + gender.c + age.c + lang.stat.c  + celf5.c , data=masked_diffscore_data) # to determine whether CELF-5 CLS significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat,diffscoresmaskedm3.gender.age.langstat.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender.age.langstat.celf over diffscoresmaskedm3.gender.age.langstat

diffscoresmaskedm3.gender.age.langstat.celf.nwrppc <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere + gender.c + age.c + lang.stat.c + celf5.c  + nwr.ppc.arc.c , data=masked_diffscore_data) # to determine whether NWR PPC significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat.celf,diffscoresmaskedm3.gender.age.langstat.celf.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrppc over diffscoresmaskedm3.gender.age.langstat.celf

diffscoresmaskedm3.gender.age.langstat.celf.nwrpcc <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c  +  nwr.pcc.arc.c , data=masked_diffscore_data) # to determine whether NWR PCC significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat.celf,diffscoresmaskedm3.gender.age.langstat.celf.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrpcc over diffscoresmaskedm3.gender.age.langstat.celf; comparing models to see whether including nwrppc or nwrpcc leads to a better fitting model

anova(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc,diffscoresmaskedm3.gender.age.langstat.celf.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrppc over diffscoresmaskedm3.gender.age.langstat.celf.nwrppc

diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c + nwr.ppc.arc.c  +  toni.c , data=masked_diffscore_data) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc,diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni over diffscoresmaskedm3.gender.age.langstat.celf.nwrppc

diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c + nwr.ppc.arc.c + toni.c  +  wrmt.c , data=masked_diffscore_data) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni,diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt over diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni

diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.flanker <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c + nwr.ppc.arc.c + toni.c + wrmt.c  +  flanker.c , data=masked_diffscore_data) # to determine whether Flanker Standard Score significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt, diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt over diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.flanker

diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c + nwr.ppc.arc.c + toni.c + wrmt.c  +  hand.c , data=masked_diffscore_data) # to determine whether handedness significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt,diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness over diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt

diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c + nwr.ppc.arc.c + toni.c + wrmt.c +  hand.c  +  pvt , data=masked_diffscore_data) # to determine whether prime visibility threshold significantly improves model fit
anova(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness,diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt)  # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt over diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness
```

##### Diff Score as DV
FINAL MODEL:
diffscoresmaskedm6 <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + (1+Experimental.Condition|Participant.ID) , data=masked_diffscore_data
```{r}
diffscoresmaskedm6.gender <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + gender.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.gender

diffscoresmaskedm6.age <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + age.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.age

diffscoresmaskedm6.langstat <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere  + lang.stat.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model--> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.langstat

diffscoresmaskedm6.celf <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere  + celf5.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.celf

diffscoresmaskedm6.nwrppc <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + nwr.ppc.arc.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.nwrppc

diffscoresmaskedm6.nwrpcc <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere+  nwr.pcc.arc.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.nwrpcc

diffscoresmaskedm6.toni <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere+  toni.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.toni

diffscoresmaskedm6.wrmt <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere+  wrmt.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.wrmt

diffscoresmaskedm6.flanker <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere+  flanker.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.flanker

diffscoresmaskedm6.handedness <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere+  hand.c + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.handedness)  # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.handedness

diffscoresmaskedm6.pvt <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere+  pvt + (1+Experimental.Condition|Participant.ID), data=masked_diffscore_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
anova(diffscoresmaskedm6,diffscoresmaskedm6.pvt)  # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer diffscoresmaskedm6 over diffscoresmaskedm6.pvt
```

### Interpreting lmers' output
#### Masked Data
##### TILLS as DV
Results:
- no sig main effects or interactions re: diff score
- N400 priming effect difference scores significantly predict TILLS Vocabulary Awareness standard scores at the level of each experimental condition, hemisphere, and region (v sus...especially since priming effect difference scores are not significant in the omnibus test...)
```{r}
masked_diffscore_data$Experimental.Condition <- contr_code_anova(masked_diffscore_data$Experimental.Condition)
masked_diffscore_data$Region <- contr_code_anova(masked_diffscore_data$Region)
masked_diffscore_data$Hemisphere <- contr_code_anova(masked_diffscore_data$Hemisphere)

diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt <- lm(tills ~ Priming.Diff.Score*Experimental.Condition*Region*Hemisphere+ gender.c + age.c + lang.stat.c + celf5.c + nwr.ppc.arc.c + toni.c + wrmt.c +  hand.c  +  pvt , data=masked_diffscore_data)
tidy(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt)%>%
  mutate(signif = stars.pval(p.value))

anova(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt)

diffscoremaskedemm1 <- emmeans(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt, ~ Priming.Diff.Score | Experimental.Condition, adjust = "none")
tidy(diffscoremaskedemm1)%>%
   mutate(signif = stars.pval(p.value))

diffscoremaskedemm2 <- emmeans(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt, ~ Priming.Diff.Score | Experimental.Condition*Hemisphere, adjust = "none")
tidy(diffscoremaskedemm2)%>%
   mutate(signif = stars.pval(p.value))

diffscoremaskedemm3 <- emmeans(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt, ~ Priming.Diff.Score | Experimental.Condition*Region, adjust = "none")
tidy(diffscoremaskedemm3)%>%
   mutate(signif = stars.pval(p.value))

diffscoremaskedemm4 <- emmeans(diffscoresmaskedm3.gender.age.langstat.celf.nwrppc.toni.wrmt.handedness.pvt, ~ Priming.Diff.Score | Experimental.Condition*Hemisphere*Region, adjust = "none")
tidy(diffscoremaskedemm4)%>%
   mutate(signif = stars.pval(p.value))


```

##### Diff Score as DV
Results:
- no sig main effects or interactions re: diff score
- TILLS Vocabulary Awareness standard scores do not significantly predict any N400 priming effect difference scores (overall, for masked word data, or for masked picture data)
```{r}
masked_diffscore_data$Experimental.Condition <- contr_code_anova(masked_diffscore_data$Experimental.Condition)
masked_diffscore_data$Region <- contr_code_anova(masked_diffscore_data$Region)
masked_diffscore_data$Hemisphere <- contr_code_anova(masked_diffscore_data$Hemisphere)

diffscoresmaskedm6 <- lmer(Priming.Diff.Score ~ tills.c*Experimental.Condition*Region*Hemisphere + (1+Experimental.Condition|Participant.ID) , data=masked_diffscore_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(diffscoresmaskedm6)%>%
  mutate(signif = stars.pval(p.value))

anova(diffscoresmaskedm6)

diffscoremaskedemm5 <- emmeans(diffscoresmaskedm6, ~ tills.c | Experimental.Condition, adjust = "none")
tidy(diffscoremaskedemm5)%>%
   mutate(signif = stars.pval(p.value))

diffscoremaskedemm6 <- emmeans(diffscoresmaskedm6, ~ tills.c | Experimental.Condition*Hemisphere, adjust = "none")
tidy(diffscoremaskedemm6)%>%
   mutate(signif = stars.pval(p.value))

diffscoremaskedemm7 <- emmeans(diffscoresmaskedm6, ~ tills.c | Experimental.Condition*Region, adjust = "none")
tidy(diffscoremaskedemm7)%>%
   mutate(signif = stars.pval(p.value))

diffscoremaskedemm8 <- emmeans(diffscoresmaskedm6, ~ tills.c | Experimental.Condition*Hemisphere*Region, adjust = "none")
tidy(diffscoremaskedemm8)%>%
   mutate(signif = stars.pval(p.value))
```


