---
title: "PADLD Analyses"
author: "Ashlie"
date: "2024-07-17"
output: html_document
---

```{r setup}

# Libraries
pacman::p_load(knitr, # rendering of .Rmd file
               lme4, # model specification/estimation
               afex, # anova and deriving p-values via LRTs from lmer
               broom.mixed, # extracting data from model fits
               faux, # generate correlated values
               tidyverse, # data wrangling and visualization 
               ggridges, # visualization
               viridis, # color schemes for visualization
               kableExtra, # helps with knitting the .Rmd file
               cowplot, # visualization tool to include multiple plots
               ggrain, # visualization tool for raincloud plots
               dplyr, # data manipulation tools
               here, # controlling directories/reproducibility
               tidyr, # formatting package
               readr, # data importation
               Hmisc, # visualization
               emmeans, # estimation of marginal means and contrasts
               sjstats, # estimation of marginal means and contrasts
               lmerTest, # deriving p-values from lmer
               MuMIn, # ?
               sjPlot, # APA formatting of numerical output
               car, # data wrangling and visualization,
               magrittr, # to use %>%
               ggpubr, # ? (Rose had it in her script)
               broom, # ? (Rose had it in her script)
               Matrix, # model specification/estimation,
               multcomp, # multiple comparison adjustments
               forcats, # organizing visualizations
               gtools, # data manipulation/wrangling
               fuzzySim, # FDR correction,
               ez, # anova
               apaTables, # visualization of anova output
               #renv # package versioning/reproducibility
               )

# Global theme set
set.seed(1234) # set random seed for reproducibility

knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)

#theme_set(theme_bw(base_size = 13) + theme(text = element_text(size=13), 
                             #axis.title=element_text(size=12),
                             #strip.text = element_text(margin=margin(2,0,2,0)), 
                             #panel.grid = element_blank()))

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE, fig.width=10, fig.height=8, fig.fullwidth=TRUE)

plot_theme <- 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18), 
        axis.text.x = element_text(size = 13), 
        axis.title.x = element_text(size = 13), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 13),
        strip.background = element_rect(color="white", fill="white", linewidth = 1.5, linetype="solid"))

options(scipen=999)
```

# All Critical Target Data

## Data Manipulation
```{r}
# Load data (1 data frame)
crittarg_data <- read.csv(here("PADLD Data", "All PADLD Critical Target Mean Amps.csv"),stringsAsFactors=TRUE) # mean amplitudes for all critical targets

crittarg_data %<>%
  mutate(Mean.Amp = as.numeric(Mean.Amp),
         Channel = factor(Channel),
         Region = factor(Region, levels=c("frontal","central","parietal","occipital")),
         Hemisphere = factor(Hemisphere, levels=c("left","midline","right")),
         Priming=factor(Priming, levels=c("unprimed","primed")),
         ISI = factor(ISI,levels=c("67","317")),
         Priming.Condition = factor(Priming.Condition, levels=c("unprimed 67","primed 67","unprimed 317","primed 317")),
         Experimental.Condition = factor(Experimental.Condition),
         Stimulus.Type = factor(Stimulus.Type),
         Prime.Visibility = factor (Prime.Visibility),
         Trial.Type = factor(Trial.Type),
         Group = factor(Group), 
         gender.c = as.numeric(Gender) - 1.5,
         Detailed.Language.Status = factor(Detailed.Language.Status),
         Language.Status = factor(Language.Status,levels=c("English monolingual","English primary")),
         lang.stat.c = as.numeric(Language.Status) - 1.5,
         Bilingual.Type = factor(Bilingual.Type),
         celf5 = as.numeric(CELF5.CLS),
         celf5.c = as.numeric(scale(CELF5.CLS, center = TRUE, scale = FALSE)),
         age.c = as.numeric(scale(Average.Age, center = TRUE, scale = FALSE)),
         nwr.ppc.arc = asin(sqrt(as.numeric(NWR.PPC)/100)),
         nwr.ppc.arc.c = as.numeric(scale(nwr.ppc.arc, center = TRUE, scale = FALSE)),
         nwr.pcc.arc = asin(sqrt(as.numeric(NWR.PCC)/100)),
         nwr.pcc.arc.c = as.numeric(scale(nwr.pcc.arc, center = TRUE, scale = FALSE)),
         tills= as.numeric(TILLS.VA.Standard.Score),
         tills.c = as.numeric(scale(TILLS.VA.Standard.Score, center = TRUE, scale = FALSE)),
         toni= as.numeric(TONI.Deviation.Quotient),
         toni.c = as.numeric(scale(TONI.Deviation.Quotient, center = TRUE, scale = FALSE)),
         wrmt = as.numeric(WRMT.LWI.Standard.Score),
         wrmt.c = as.numeric(scale(WRMT.LWI.Standard.Score, center = TRUE, scale = FALSE)),
         flanker = as.numeric(Flanker.Standard.Score),
         flanker.c = as.numeric(scale(Flanker.Standard.Score, center = TRUE, scale = FALSE)),
         handedness = factor(Handedness),
         hand.c = as.numeric(handedness) - 1.5,
         pvt = factor(PVT,levels=c("50","67","83","100","> 117")))
str(crittarg_data)

# Create some data subsets
piccrittarg_data <- subset(crittarg_data,Experimental.Condition == "picture")
wordcrittarg_data <- subset(crittarg_data,Experimental.Condition == "word")
maskedpic_data <- subset(crittarg_data,Experimental.Condition == "picture" & Prime.Visibility == "masked")
maskedword_data <- subset(crittarg_data,Experimental.Condition == "word" & Prime.Visibility == "masked")
vispic_data <- subset(crittarg_data,Experimental.Condition == "picture" & Prime.Visibility == "visible")
visword_data <- subset(crittarg_data,Experimental.Condition == "word" & Prime.Visibility == "visible")
DLD_data <- subset(crittarg_data,Group == "DLD")
TL_data <- subset(crittarg_data,Group == "TL")
dldmaskedpic_data <- subset(crittarg_data,Experimental.Condition == "picture" & Prime.Visibility == "masked" & Group == "DLD")
dldmaskedword_data <- subset(crittarg_data,Experimental.Condition == "word" & Prime.Visibility == "masked" & Group == "DLD")
dldvispic_data <- subset(crittarg_data,Experimental.Condition == "picture" & Prime.Visibility == "visible" & Group == "DLD")
dldvisword_data <- subset(crittarg_data,Experimental.Condition == "word" & Prime.Visibility == "visible" & Group == "DLD")
tlmaskedpic_data <- subset(crittarg_data,Experimental.Condition == "picture" & Prime.Visibility == "masked" & Group == "TL")
tlmaskedword_data <- subset(crittarg_data,Experimental.Condition == "word" & Prime.Visibility == "masked" & Group == "TL")
tlvispic_data <- subset(crittarg_data,Experimental.Condition == "picture" & Prime.Visibility == "visible" & Group == "TL")
tlvisword_data <- subset(crittarg_data,Experimental.Condition == "word" & Prime.Visibility == "visible" & Group == "TL")

# Notes:
# Region = anteriority/posteriority; default reference level (set above) = frontal
# Hemisphere = laterality; default reference level (set above) = left
# Priming = primed vs. unprimed; default reference level (set above) = unprimed
# ISI = 67 vs. 317; default reference level (set above) = 67
# Priming Condition = Priming + ISI; default reference level (set above) = unprimed 67
# Experimental Condition = picture vs. word; default reference level = picture
# Stimulus Type = prime vs. target; default reference level = prime (when present)
# Prime Visibility = masked vs. visible; default reference level = masked
# Trial Type = critical vs. probe; default reference level = critical
# Group = DLD vs. TL; default reference level = DLD
# For gender, female = -0.5 (after centering), male = 0.5 (after centering)
# Detailed Language Status = language status + bilingual type (see below); default reference level= English monolingual
# Language Status = English monolingual vs. English primary; default reference level (set above) \ = English monolingual
# For language status, English monolingual = -0.5 (after centering), English primary/bilingual = 0.5 (after centering)
# Bilingual Type = sequential vs. simultaneous and the languages spoken; default reference level = NA? sequential bilingual (English-French)?
# For handedness, L = -0.5 (after centering), R = 0.5 (after centering)
# PVT = prime visibility threshold (shortest prime duration at which participant identified > 50% of animal primes presented at that duration); 50 vs. 67 vs. 83 vs. 100 vs. > 117; default reference level (set above) = 50
```

## Descriptives
```{r}
# N400 mean amplitudes by group, priming condition, experimental condition, and prime visibility (collapsed across region and hemisphere)
crittarg_data_grouped1 <- group_by(crittarg_data, Experimental.Condition, Group, Prime.Visibility, Priming, ISI)
summarise(crittarg_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

# N400 mean amplitudes by group, priming condition, experimental condition, and prime visibility
crittarg_data_grouped2 <- group_by(crittarg_data, Experimental.Condition, Group, Prime.Visibility, Priming, ISI, Region, Hemisphere)
summarise(crittarg_data_grouped2, # summarize operation by group
  mean = mean(Mean.Amp),
  std = sd(Mean.Amp)
    )

# # Mean amplitude by group and priming condition (for specific region and hemisphere)
# crittarg_data %>%
#   filter(Region == "central")%>% #& Hemisphere == "right")%>%
#   group_by(Group, Priming.Condition)%>%
#   summarise_at('Mean.Amp', 
#                list(~mean(., na.rm=T), 
#                     ~sd(., na.rm=T),
#                     ~median(., na.rm=T),
#                     ~min(., na.rm=T),
#                     ~max(., na.rm=T),
#                     ~sum(!is.na(.))))%>%
#   dplyr::rename("n" = "sum")%>%
#   dplyr::select(Group, Priming.Condition, n, mean, sd, median, min, max)%>%
#   mutate(total.n = sum(n))%>%
#   knitr::kable()
```


## Visualizations
```{r}
# N400 mean amplitude by (collapsed across experimental condition, group, prime visibility, priming condition, region, and hemisphere)
hist(crittarg_data$Mean.Amp)
boxplot(crittarg_data$Mean.Amp)

# N400 mean amplitude by experimental condition (collapsed across group, prime visibility, priming condition, region, and hemisphere)
plot(Mean.Amp ~ Experimental.Condition, data = crittarg_data)

# N400 mean amplitude by group (collapsed acrossexperimental condition, prime visibility, priming condition, region, and hemisphere)
plot(Mean.Amp ~ Group, data = crittarg_data)

# N400 mean amplitude by group and priming condition and region  (collapsed across hemisphere) for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and region (collapsed across hemisphere) for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data (collapsed across hemisphere)")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~ factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for masked picture data
maskedpic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Picture Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for masked word data
maskedword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Masked Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for visible picture data
vispic_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Picture Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

# N400 mean amplitude by group and priming condition and hemisphere and region for visible word data
visword_data %>%
  ggplot(aes(x=Priming, y=Mean.Amp, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ggtitle("Visible Word Data")+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("frontal","central","parietal","occipital")) + ISI)

```


## Analyses
### ANOVA analyses
I can't get the emmeans to run for some of these models, and I'm partial to lmers anyway.
```{r}
## DLD ANOVAs ##
options(contrasts = c("contr.sum", "contr.poly")) # contrast code doesn't work without this but you don't need it to just run the anova
DLDmaskedwordanova <-ezANOVA(data=dldmaskedword_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
       # within_covariates = .(Gender,Language.Status,celf5,Average.Age,nwr.ppc.arc,tills,toni,wrmt,flanker,pvt,handedness),
        type=3,
        return_aov=TRUE) # because i need this for yet more post hocs
DLDmaskedwordanova_table <- apa.ezANOVA.table(DLDmaskedwordanova)
print(DLDmaskedwordanova)
DLDmaskedwordemm <- emmeans(DLDmaskedwordanova$aov, ~ Priming*ISI | Region)
DLDmaskedwordemm # this will give me cell means and confidence intervals around them
# all pairwise comparisons 
tidy(pairs(DLDmaskedwordemm, adjust="none"))%>%
  mutate(signif = stars.pval(p.value))

DLDviswordanova <-ezANOVA(data=dldvisword_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
        type=3)
DLDviswordanova_table <- apa.ezANOVA.table(DLDviswordanova)
print(DLDviswordanova)
# DLDviswordemm <- emmeans(DLDviswordanova$aov, ~ Priming*ISI | Region)
# DLDviswordemm # this will give me cell means and confidence intervals around them
# # all pairwise comparisons 
# tidy(pairs(DLDviswordemm, adjust="none"))%>%
#   mutate(signif = stars.pval(p.value))

DLDmaskedpicanova <-ezANOVA(data=dldmaskedpic_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
        type=3)
DLDmaskedpicanova_table <- apa.ezANOVA.table(DLDmaskedpicanova)
print(DLDmaskedpicanova)
# DLDmaskedpicemm <- emmeans(DLDmaskedpicanova$aov, ~ Priming*ISI | Region)
# DLDmaskedpicemm # this will give me cell means and confidence intervals around them
# # all pairwise comparisons 
# tidy(pairs(DLDmaskedpicemm, adjust="none"))%>%
#   mutate(signif = stars.pval(p.value))

DLDvispicanova <-ezANOVA(data=dldvispic_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
        type=3)
DLDvispicanova_table <- apa.ezANOVA.table(DLDvispicanova)
print(DLDvispicanova)
DLDvispicemm1 <- emmeans(DLDvispicanova$aov, ~ Priming| Region)
DLDvispicemm2 <- emmeans(DLDvispicanova$aov, ~ ISI | Region)
#DLDvispicemm3 <- emmeans(DLDvispicanova$aov, ~ Priming*ISI | Region)
#DLDvispicemm # this will give me cell means and confidence intervals around them
# all pairwise comparisons 
tidy(pairs(DLDvispicemm1, adjust="none"))%>%    
  mutate(signif = stars.pval(p.value))
tidy(pairs(DLDvispicemm2, adjust="none"))%>%    
  mutate(signif = stars.pval(p.value))
tidy(pairs(DLDvispicemm3, adjust="none"))%>%    
  mutate(signif = stars.pval(p.value))

## TL ANOVAs ##
TLmaskedwordanova <-ezANOVA(data=tlmaskedword_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
        type=3)
TLmaskedwordanova_table <- apa.ezANOVA.table(TLmaskedwordanova)
print(TLmaskedwordanova)
TLmaskedwordemm <- emmeans(TLmaskedwordanova$aov, ~ Priming*ISI | Region)
TLmaskedwordemm # this will give me cell means and confidence intervals around them
# all pairwise comparisons 
tidy(pairs(TLmaskedwordemm, adjust="none"))%>%    
  mutate(signif = stars.pval(p.value))

TLviswordanova <-ezANOVA(data=tlvisword_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
        type=3)
TLviswordanova_table <- apa.ezANOVA.table(TLviswordanova)
print(TLviswordanova)
TLviswordemm <- emmeans(TLviswordanova$aov, ~ Priming*ISI | Region)
TLviswordemm # this will give me cell means and confidence intervals around them
# all pairwise comparisons 
tidy(pairs(TLviswordemm, adjust="none"))%>%    
  mutate(signif = stars.pval(p.value))

TLmaskedpicanova <-ezANOVA(data=tlmaskedpic_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
        type=3)
TLmaskedpicanova_table <- apa.ezANOVA.table(TLmaskedpicanova)
print(TLmaskedpicanova)
TLmaskedpicemm <- emmeans(TLmaskedpicanova$aov, ~ Priming*ISI | Region)
TLmaskedpicemm # this will give me cell means and confidence intervals around them
# all pairwise comparisons 
tidy(pairs(TLmaskedpicemm, adjust="none"))%>%    
  mutate(signif = stars.pval(p.value))

TLvispicanova <-ezANOVA(data=tlvispic_data,
        dv=Mean.Amp, # column name for dependent measure
        wid=.(Participant.ID), # name of random factor, either subject or item
        within=.(Priming,ISI,Region,Hemisphere), # within-subjects variable
        type=3)
TLvispicanova_table <- apa.ezANOVA.table(TLvispicanova)
print(TLvispicanova)
TLvispicemm <- emmeans(TLvispicanova$aov, ~ Priming*ISI | Region)
TLvispicemm # this will give me cell means and confidence intervals around them
# all pairwise comparisons 
tidy(pairs(TLvispicemm, adjust="none"))%>%    
  mutate(signif = stars.pval(p.value))
```

### Finding the maximal convergent model (Prime*ISI*Region*Hemisphere)
#### DLD data
##### Masked Word Data
FINAL BASE MODEL: DLDmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data
```{r}
DLDmaskedwordm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(DLDmaskedwordm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

DLDmaskedwordm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

DLDmaskedwordm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the better fit of the two
anova(DLDmaskedwordm3,DLDmaskedwordm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDmaskedwordm3 over DLDmaskedwordm2; continuing to build random effects

DLDmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the better fit of the two
anova(DLDmaskedwordm3,DLDmaskedwordm4) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDmaskedwordm4 over DLDmaskedwordm3; now to test the covariates!
```
##### Masked Picture Data
FINAL BASE MODEL: DLDmaskedpicm6 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data
```{r}
DLDmaskedpicm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(DLDmaskedpicm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

DLDmaskedpicm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

DLDmaskedpicm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(DLDmaskedpicm3,DLDmaskedpicm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDmaskedpicm3 over DLDmaskedpicm2; continuing to build random effects

DLDmaskedpicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so seeing how a ranodm slope of ISI compares to a random slope of Priming

DLDmaskedpicm5 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(DLDmaskedpicm3,DLDmaskedpicm5) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm3 over DLDmaskedpicm5; double checking an additive random slope isn't better since models with each variable alone converged but not when they interacted

DLDmaskedpicm6 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(DLDmaskedpicm3,DLDmaskedpicm6) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDmaskedpicm6 over DLDmaskedpicm3; now to test the covariates!
```
##### Visible Word Data
FINAL BASE MODEL: DLDviswordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldvisword_data
```{r}
DLDviswordm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(DLDviswordm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

DLDviswordm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

DLDviswordm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(DLDviswordm3,DLDviswordm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDviswordm3 over DLDviswordm2; continuing to buid the random effects

DLDviswordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(DLDviswordm3,DLDviswordm4) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDviswordm4 over DLDviswordm3; now to test the covariates!
```
##### Visible Picture Data
FINAL BASE MODEL:DLDvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+ISI|Participant.ID), data=dldvispic_data
```{r}
DLDvispicm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(DLDvispicm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

DLDvispicm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

DLDvispicm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(DLDvispicm3,DLDvispicm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm2 over DLDvispicm3; continuing to build random effects

DLDvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
# converges! comparing models to ensure this model has the best fit of the two
anova(DLDvispicm4,DLDvispicm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDvispicm4 over DLDvispicm2; double checking that an interactive random slope isn't better

DLDvispicm5 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, double checking that an additive random slope also isn't better

DLDvispicm6 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(DLDvispicm4,DLDvispicm6) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer DLDvispicm4 over DLDvispicm6; now to test the covariates!
```
#### TL data
##### Masked Word Data
FINAL BASE MODEL: TLmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data
```{r}
TLmaskedwordm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(TLmaskedwordm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

TLmaskedwordm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

TLmaskedwordm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLmaskedwordm3,TLmaskedwordm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLmaskedwordm3 over TLmaskedwordm2; continuing to build random effects

TLmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLmaskedwordm3,TLmaskedwordm4) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLmaskedwordm4 over TLmaskedwordm3; now to test the covariates!
```
##### Masked Picture Data
FINAL BASE MODEL:TLmaskedpicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data
```{r}
TLmaskedpicm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(TLmaskedpicm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

TLmaskedpicm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

TLmaskedpicm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLmaskedpicm3,TLmaskedpicm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLmaskedpicm3 over TLmaskedpicm2; continuing to build random effects

TLmaskedpicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLmaskedpicm3,TLmaskedpicm4) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLmaskedpicm4 over TLmaskedpicm3; now to test the covariates!
```
##### Visible Word Data
FINAL BASE MODEL: TLviswordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlvisword_data
```{r}
TLviswordm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # isSingular warning, so checking random effects' variances
summary(rePCA(TLviswordm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

TLviswordm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

TLviswordm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLviswordm3,TLviswordm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLviswordm3 over TLviswordm2; continuing to build random effects

TLviswordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLviswordm3,TLviswordm4) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLviswordm4 over TLviswordm3; now to test the covariates!
```
##### Visible Picture Data
FINAL BASE MODEL: TLvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlvispic_data
```{r}
TLvispicm1 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID)+ (1|Channel), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))# isSingular warning, so checking random effects' variances
summary(rePCA(TLvispicm1)) # PCA results indicate no variability in the random effects for Channel, so trying a model with that random effect removed

TLvispicm2 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! now building random effects

TLvispicm3 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLvispicm3,TLvispicm2) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLvispicm3 over TLvispicm2

TLvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # converges! comparing models to ensure this model has the best fit of the two
anova(TLvispicm3,TLvispicm4) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLvispicm4 over TLvispicm3; now to test the covariates!
```

### Testing impact of covariates (Prime*ISI*Region*Hemisphere)
#### DLD data
##### Masked Word Data
FINAL MODEL: DLDmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data
```{r}
DLDmaskedwordm4.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.gender

DLDmaskedwordm4.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.age

DLDmaskedwordm4.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.langstat

DLDmaskedwordm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.celf

DLDmaskedwordm4.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + nwr.ppc.arc.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.nwrppc

DLDmaskedwordm4.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  nwr.pcc.arc.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.nwrpcc

DLDmaskedwordm4.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  tills.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(DLDmaskedwordm4, DLDmaskedwordm4.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.tills

DLDmaskedwordm4.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  toni.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.toni

DLDmaskedwordm4.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  wrmt.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.wrmt

DLDmaskedwordm4.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  flanker.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(DLDmaskedwordm4,DLDmaskedwordm4.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedwordm4 over DLDmaskedwordm4.flanker

#DLDmaskedwordm4.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  hand.c + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
#anova(DLDmaskedwordm4,DLDmaskedwordm4.handedness) # all DLD participants are right handed so handedness is completely redundant and, thus, cannot improve model fit --> prefer DLDmaskedwordm4 over DLDmaskedwordm4.handedness

DLDmaskedwordm4.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  pvt + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
#anova(DLDmaskedwordm4,DLDmaskedwordm4.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> DLDmaskedwordm4.pvt has a (near) singular fit, so prefer DLDmaskedwordm4 over DLDmaskedwordm4.pvt
```
##### Masked Picture Data
FINAL MODEL: DLDmaskedpicm6 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data
```{r}
DLDmaskedpicm6.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.gender

DLDmaskedpicm6.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.age

DLDmaskedpicm6.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.langstat

DLDmaskedpicm6.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.celf

DLDmaskedpicm6.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + nwr.ppc.arc.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.nwrppc

DLDmaskedpicm6.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  nwr.pcc.arc.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.nwrpcc

DLDmaskedpicm6.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  tills.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(DLDmaskedpicm6, DLDmaskedpicm6.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.tills

DLDmaskedpicm6.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  toni.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.toni

DLDmaskedpicm6.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  wrmt.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.wrmt

DLDmaskedpicm6.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  flanker.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.flanker

#DLDmaskedpicm6.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  hand.c + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
#anova(DLDmaskedpicm6,DLDmaskedpicm6.handedness) # all DLD participants are right handed so handedness is completely redundant and, thus, cannot improve model fit --> prefer DLDmaskedpicm6 over DLDmaskedpicm6.handedness

DLDmaskedpicm6.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  pvt + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
anova(DLDmaskedpicm6,DLDmaskedpicm6.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDmaskedpicm6 over DLDmaskedpicm6.pvt
```
##### Visible Word Data
FINAL MODEL: DLDviswordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldvisword_data
```{r}
DLDviswordm4.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.gender

DLDviswordm4.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.age

DLDviswordm4.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.langstat

DLDviswordm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.celf

DLDviswordm4.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + nwr.ppc.arc.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.nwrppc

DLDviswordm4.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  nwr.pcc.arc.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.nwrpcc

DLDviswordm4.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  tills.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(DLDviswordm4, DLDviswordm4.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.tills

DLDviswordm4.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  toni.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDviswordm4 over DLDviswordm4.toni

DLDviswordm4.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  wrmt.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
# anova(DLDviswordm4,DLDviswordm4.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> DLDviswordm4.wrmt has (near) singular fit, so prefer DLDviswordm4 over DLDviswordm4.wrmt

DLDviswordm4.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  flanker.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
#anova(DLDviswordm4,DLDviswordm4.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> DLDviswordm4.flanker has (near) singular fit, so  prefer DLDviswordm4 over DLDviswordm4.flanker

#DLDviswordm4.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  hand.c + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
#anova(DLDviswordm4,DLDviswordm4.handedness) # all DLD participants are right handed so handedness is completely redundant and, thus, cannot improve model fit --> prefer DLDviswordm4 over DLDviswordm4.handedness

DLDviswordm4.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  pvt + (1+Priming*ISI|Participant.ID), data=dldvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
anova(DLDviswordm4,DLDviswordm4.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model -->  DLDviswordm4.pvt has (near) singular fit, so  prefer DLDviswordm4 over DLDviswordm4.pvt
```
##### Visible Picture Data
FINAL MODEL: DLDvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+ISI|Participant.ID), data=dldvispic_data
```{r}
DLDvispicm4.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.gender

DLDvispicm4.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.age

DLDvispicm4.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.langstat

DLDvispicm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.celf

DLDvispicm4.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + nwr.ppc.arc.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.nwrppc

DLDvispicm4.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  nwr.pcc.arc.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.nwrpcc

DLDvispicm4.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  tills.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(DLDvispicm4, DLDvispicm4.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.tills

DLDvispicm4.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  toni.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.toni

DLDvispicm4.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  wrmt.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.wrmt

DLDvispicm4.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  flanker.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(DLDvispicm4,DLDvispicm4.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer DLDvispicm4 over DLDvispicm4.flanker

#DLDvispicm4.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  hand.c + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
#anova(DLDvispicm4,DLDvispicm4.handedness) # all DLD participants are right handed so handedness is completely redundant and, thus, cannot improve model fit --> prefer DLDvispicm4 over DLDvispicm4.handedness

DLDvispicm4.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + pvt + (1+ISI|Participant.ID), data=dldvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
#anova(DLDvispicm4,DLDvispicm4.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model -->  DLDviswordm4.pvt has (near) singular fit, so prefer DLDvispicm4 over DLDvispicm4.pvt
```

#### TL data
##### Masked Word Data
FINAL MODEL: TLmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere +(1+Priming*ISI|Participant.ID), data=tlmaskedword_data
```{r}
TLmaskedwordm4.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.gender

TLmaskedwordm4.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.age

TLmaskedwordm4.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.langstat

TLmaskedwordm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.celf

TLmaskedwordm4.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere +nwr.ppc.arc.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.nwrppc

TLmaskedwordm4.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + nwr.pcc.arc.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.nwrpcc

TLmaskedwordm4.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + tills.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(TLmaskedwordm4, TLmaskedwordm4.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.tills

TLmaskedwordm4.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + toni.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.toni

TLmaskedwordm4.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + wrmt.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.wrmt

TLmaskedwordm4.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + flanker.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.flanker

TLmaskedwordm4.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + hand.c + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.handedness) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.handedness

TLmaskedwordm4.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + pvt + (1+Priming*ISI|Participant.ID), data=tlmaskedword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
anova(TLmaskedwordm4,TLmaskedwordm4.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedwordm4 over TLmaskedwordm4.pvt
```
##### Masked Picture Data
FINAL MODEL: TLmaskedpicm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data
```{r}
TLmaskedpicm4.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(TLmaskedpicm4,TLmaskedpicm4.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4 over TLmaskedpicm4.gender

TLmaskedpicm4.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(TLmaskedpicm4,TLmaskedpicm4.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4 over TLmaskedpicm4.age

TLmaskedpicm4.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(TLmaskedpicm4,TLmaskedpicm4.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4 over TLmaskedpicm4.langstat

TLmaskedpicm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(TLmaskedpicm4,TLmaskedpicm4.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4

TLmaskedpicm4.celf.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c + nwr.ppc.arc.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(TLmaskedpicm4.celf,TLmaskedpicm4.celf.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.nwrppc

TLmaskedpicm4.celf.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c +  nwr.pcc.arc.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(TLmaskedpicm4.celf,TLmaskedpicm4.celf.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.nwrpcc

TLmaskedpicm4.celf.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c +  tills.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(TLmaskedpicm4.celf, TLmaskedpicm4.celf.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.tills

TLmaskedpicm4.celf.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c +  toni.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(TLmaskedpicm4.celf,TLmaskedpicm4.celf.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.toni

TLmaskedpicm4.celf.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c +  wrmt.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(TLmaskedpicm4.celf,TLmaskedpicm4.celf.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.wrmt

TLmaskedpicm4.celf.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c +  flanker.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(TLmaskedpicm4.celf,TLmaskedpicm4.celf.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.flanker

TLmaskedpicm4.celf.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c +  hand.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
anova(TLmaskedpicm4.celf,TLmaskedpicm4.celf.handedness)  # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.handedness

TLmaskedpicm4.celf.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + celf5.c +  pvt + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
anova(TLmaskedpicm4.celf,TLmaskedpicm4.celf.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLmaskedpicm4.celf over TLmaskedpicm4.celf.pvt
```
##### Visible Word Data
FINAL MODEL: TLviswordm4.langstat.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  +  wrmt.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data
```{r}
TLviswordm4.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(TLviswordm4,TLviswordm4.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4 over TLviswordm4.gender

TLviswordm4.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(TLviswordm4,TLviswordm4.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4 over TLviswordm4.age

TLviswordm4.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(TLviswordm4,TLviswordm4.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLviswordm4.langstat over TLviswordm4 

TLviswordm4.langstat.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c + celf5.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(TLviswordm4.langstat,TLviswordm4.langstat.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat over TLviswordm4.langstat.celf

TLviswordm4.langstat.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c   + nwr.ppc.arc.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(TLviswordm4.langstat,TLviswordm4.langstat.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat over TLviswordm4.langstat.nwrppc

TLviswordm4.langstat.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  +  nwr.pcc.arc.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(TLviswordm4.langstat,TLviswordm4.langstat.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat over TLviswordm4.langstat.nwrpcc

TLviswordm4.langstat.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  +  tills.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(TLviswordm4.langstat, TLviswordm4.langstat.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat over TLviswordm4.langstat.tills

TLviswordm4.langstat.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  +  toni.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(TLviswordm4.langstat,TLviswordm4.langstat.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat over TLviswordm4.langstat.toni

TLviswordm4.langstat.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  +  wrmt.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(TLviswordm4.langstat,TLviswordm4.langstat.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> significant: prefer TLviswordm4.langstat.wrmt over TLviswordm4.langstat

TLviswordm4.langstat.wrmt.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  + wrmt.c +   flanker.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(TLviswordm4.langstat.wrmt,TLviswordm4.langstat.wrmt.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat.wrmt over TLviswordm4.langstat.wrmt.flanker

TLviswordm4.langstat.wrmt.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  + wrmt.c +   hand.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
anova(TLviswordm4.langstat.wrmt,TLviswordm4.langstat.wrmt.handedness) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat.wrmt over TLviswordm4.langstat.wrmt.handedness

TLviswordm4.langstat.wrmt.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  + wrmt.c +   pvt + (1+Priming*ISI|Participant.ID), data=tlvisword_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
anova(TLviswordm4.langstat.wrmt,TLviswordm4.langstat.wrmt.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLviswordm4.langstat.wrmt over TLviswordm4.langstat.wrmt.pvt
```
##### Visible Picture Data
FINAL MODEL: TLvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlvispic_data
```{r}
TLvispicm4.gender <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + gender.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether gender significantly improves model fit
anova(TLvispicm4,TLvispicm4.gender)# the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.gender

TLvispicm4.age <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + age.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether age significantly improves model fit
anova(TLvispicm4,TLvispicm4.age) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.age

TLvispicm4.langstat <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + lang.stat.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether language status significantly improves model fit
anova(TLvispicm4,TLvispicm4.langstat) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> TLvispicm4.langstat has (near) singular fit, so prefer TLvispicm4 over TLvispicm4.langstat

TLvispicm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether CELF-5 CLS significantly improves model fit
anova(TLvispicm4,TLvispicm4.celf) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.celf

TLvispicm4.nwrppc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + nwr.ppc.arc.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PPC significantly improves model fit
anova(TLvispicm4,TLvispicm4.nwrppc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.nwrppc

TLvispicm4.nwrpcc <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  nwr.pcc.arc.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether NWR PCC significantly improves model fit
anova(TLvispicm4,TLvispicm4.nwrpcc) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.nwrpcc

TLvispicm4.tills <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  tills.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TILLS VA Standard Score significantly improves model fit
anova(TLvispicm4, TLvispicm4.tills) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.tills

TLvispicm4.toni <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  toni.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether TONI Deviation Quotient significantly improves model fit
anova(TLvispicm4,TLvispicm4.toni) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.toni

TLvispicm4.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  wrmt.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether WRMT LWI Standard Score significantly improves model fit
anova(TLvispicm4,TLvispicm4.wrmt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.wrmt

TLvispicm4.flanker <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  flanker.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether Flanker Standard Score significantly improves model fit
anova(TLvispicm4,TLvispicm4.flanker) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.flanker

TLvispicm4.handedness <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere+  hand.c + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether handedness significantly improves model fit
anova(TLvispicm4,TLvispicm4.handedness) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.handedness

TLvispicm4.pvt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + pvt + (1+Priming*ISI|Participant.ID), data=tlvispic_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) # to determine whether prime visibility threshold significantly improves model fit
anova(TLvispicm4,TLvispicm4.pvt) # the smaller/lower the AIC and/or BIC value, the “better” is the predictive performance of the model; a very small p-value (< .001) means that adding the additional IVs to the model leads to a significantly improved fit over the reduced model --> not significant: prefer TLvispicm4 over TLvispicm4.pvt
```

### Interpreting lmers' output (Prime*ISI*Region*Hemisphere)
#### DLD data
##### Masked Word Data
Results:
- sig interaction of priming x region but no sig diffs btw priming conditions (overall, by hemisphere, by region, or by hemisphere and region)
```{r}
dldmaskedword_data$Priming <- contr_code_anova(dldmaskedword_data$Priming)
dldmaskedword_data$ISI <- contr_code_anova(dldmaskedword_data$ISI)
dldmaskedword_data$Region <- contr_code_anova(dldmaskedword_data$Region)
dldmaskedword_data$Hemisphere <- contr_code_anova(dldmaskedword_data$Hemisphere)

DLDmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldmaskedword_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
anova(DLDmaskedwordm4)
tidy(DLDmaskedwordm4)%>%
  mutate(signif = stars.pval(p.value))

emm1 <- emmeans(DLDmaskedwordm4, pairwise ~ Priming | Region,adjust = "none")
emm1

DLDmaskedwordemm1 <- emmeans(DLDmaskedwordm4, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedwordemm1, contrast_spec)

# Convert to a data frame and add significance stars
dldmaskedwordcontrast_df1 <- as.data.frame(summary(contrast_results))
dldmaskedwordcontrast_df1$p_value_stars <- cut(dldmaskedwordcontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDmaskedwordemm2 <- emmeans(DLDmaskedwordm4, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedwordemm2, contrast_spec)

# Convert to a data frame and add significance stars
dldmaskedwordcontrast_df2 <- as.data.frame(summary(contrast_results))
dldmaskedwordcontrast_df2$p_value_stars <- cut(dldmaskedwordcontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

DLDmaskedwordemm3 <- emmeans(DLDmaskedwordm4, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedwordemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
dldmaskedwordcontrast_df3 <- as.data.frame(summary(contrast_results))
dldmaskedwordcontrast_df3$p_value_stars <- cut(dldmaskedwordcontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDmaskedwordemm4 <- emmeans(DLDmaskedwordm4, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedwordemm4, contrast_spec)

# Convert to a data frame and add significance stars
dldmaskedwordcontrast_df4 <- as.data.frame(summary(contrast_results))
dldmaskedwordcontrast_df4$p_value_stars <- cut(dldmaskedwordcontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
dldmaskedwordcombined_df <- bind_rows(dldmaskedwordcontrast_df1, dldmaskedwordcontrast_df2,dldmaskedwordcontrast_df3,dldmaskedwordcontrast_df4)
```
##### Masked Picture Data
Results:
- sig interactions of priming x ISI and priming x region but no sig diffs btw priming conditions when corrected for multiple comparisons (uncorrected p-value: sig priming effect at central region; p = .047)
- when corrected for multiple comparisons, no sig diffs btw priming conditions (overall, by hemisphere, by region, or by hemisphere and region)
- uncorrected p-values: sig diffs btw priming conditions at ISI 67 @ central (typical priming effect), ISI 317 @ occipital (unprimed more attenuated than primed--opposite of typical priming effect), and ISI 317 @ left occipital (unprimed more attenuated than primed--opposite of typical priming effect)
```{r}
dldmaskedpic_data$Priming <- contr_code_anova(dldmaskedpic_data$Priming)
dldmaskedpic_data$ISI <- contr_code_anova(dldmaskedpic_data$ISI)
dldmaskedpic_data$Region <- contr_code_anova(dldmaskedpic_data$Region)
dldmaskedpic_data$Hemisphere <- contr_code_anova(dldmaskedpic_data$Hemisphere)

DLDmaskedpicm6 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming+ISI|Participant.ID), data=dldmaskedpic_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(DLDmaskedpicm6)%>%
  mutate(signif = stars.pval(p.value))

anova(DLDmaskedpicm6)

emm1 <- emmeans(DLDmaskedpicm6, pairwise ~ Priming | ISI,adjust = "none")
emm1
emm2 <- emmeans(DLDmaskedpicm6, pairwise ~ Priming | Region,adjust = "none")
emm2

DLDmaskedpicemm1 <- emmeans(DLDmaskedpicm6, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedpicemm1, contrast_spec)

# Convert to a data frame and add significance stars
dldmaskedpiccontrast_df1 <- as.data.frame(summary(contrast_results))
dldmaskedpiccontrast_df1$p_value_stars <- cut(dldmaskedpiccontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDmaskedpicemm2 <- emmeans(DLDmaskedpicm6, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedpicemm2, contrast_spec)

# Convert to a data frame and add significance stars
dldmaskedpiccontrast_df2 <- as.data.frame(summary(contrast_results))
dldmaskedpiccontrast_df2$p_value_stars <- cut(dldmaskedpiccontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

DLDmaskedpicemm3 <- emmeans(DLDmaskedpicm6, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedpicemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
dldmaskedpiccontrast_df3 <- as.data.frame(summary(contrast_results))
dldmaskedpiccontrast_df3$p_value_stars <- cut(dldmaskedpiccontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDmaskedpicemm4 <- emmeans(DLDmaskedpicm6, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDmaskedpicemm4, contrast_spec)

# Convert to a data frame and add significance stars
dldmaskedpiccontrast_df4 <- as.data.frame(summary(contrast_results))
dldmaskedpiccontrast_df4$p_value_stars <- cut(dldmaskedpiccontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
dldmaskedpiccombined_df <- bind_rows(dldmaskedpiccontrast_df1, dldmaskedpiccontrast_df2,dldmaskedpiccontrast_df3,dldmaskedpiccontrast_df4)
```
##### Visible Word Data
- no sig main effect of or interactions with priming and no sig diffs btw priming conditions (overall, by hemisphere, by region, or by hemisphere and region)
```{r}
dldvisword_data$Priming <- contr_code_anova(dldvisword_data$Priming)
dldvisword_data$ISI <- contr_code_anova(dldvisword_data$ISI)
dldvisword_data$Region <- contr_code_anova(dldvisword_data$Region)
dldvisword_data$Hemisphere <- contr_code_anova(dldvisword_data$Hemisphere)

DLDviswordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=dldvisword_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(DLDviswordm4)%>%
  mutate(signif = stars.pval(p.value))

anova(DLDviswordm4)

DLDviswordemm1 <- emmeans(DLDviswordm4, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDviswordemm1, contrast_spec)

# Convert to a data frame and add significance stars
dldviswordcontrast_df1 <- as.data.frame(summary(contrast_results))
dldviswordcontrast_df1$p_value_stars <- cut(dldviswordcontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDviswordemm2 <- emmeans(DLDviswordm4, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDviswordemm2, contrast_spec)

# Convert to a data frame and add significance stars
dldviswordcontrast_df2 <- as.data.frame(summary(contrast_results))
dldviswordcontrast_df2$p_value_stars <- cut(dldviswordcontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

DLDviswordemm3 <- emmeans(DLDviswordm4, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDviswordemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
dldviswordcontrast_df3 <- as.data.frame(summary(contrast_results))
dldviswordcontrast_df3$p_value_stars <- cut(dldviswordcontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDviswordemm4 <- emmeans(DLDviswordm4, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDviswordemm4, contrast_spec)

# Convert to a data frame and add significance stars
dldviswordcontrast_df4 <- as.data.frame(summary(contrast_results))
dldviswordcontrast_df4$p_value_stars <- cut(dldviswordcontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
dldviswordcombined_df <- bind_rows(dldviswordcontrast_df1, dldviswordcontrast_df2,dldviswordcontrast_df3,dldviswordcontrast_df4)
```
##### Visible Picture Data
Results:
- sig interaction of priming x region driven by sig diffs btw priming conditions at frontal (p = .004), central (p = .003), and occipital regions (p < .001) (sig even when corrected for multiple comparisons)
- when corrected for multiple comparisons, sig diffs btw priming conditions at ISI 317 @ occipital (unprimed more attenuated than primed--opposite of typical priming effect)
- uncorrected p-values: sig diffs btw priming conditions at ISI 317 @ frontal (typical priming effect), ISI 317 @ central (typical priming effect), ISI 317 @ occipital (unprimed more attenuated than primed--opposite of typical priming effect), ISI 317 @ left occipital (unprimed more attenuated than primed--opposite of typical priming effect), ISI 317 @ midline central (typical priming effect), ISI 317 @ right frontal (typical priming effect), and ISI 317 @ right occipital (unprimed more attenuated than primed--opposite of typical priming effect)
```{r}
dldvispic_data$Priming <- contr_code_anova(dldvispic_data$Priming)
dldvispic_data$ISI <- contr_code_anova(dldvispic_data$ISI)
dldvispic_data$Region <- contr_code_anova(dldvispic_data$Region)
dldvispic_data$Hemisphere <- contr_code_anova(dldvispic_data$Hemisphere)

DLDvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+ISI|Participant.ID), data=dldvispic_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(DLDvispicm4)%>%
  mutate(signif = stars.pval(p.value))

anova(DLDvispicm4)

emm1 <- emmeans(DLDvispicm4, pairwise ~ Priming | Region,adjust = "none")
emm1


DLDvispicemm1 <- emmeans(DLDvispicm4, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDvispicemm1, contrast_spec)

# Convert to a data frame and add significance stars
dldvispiccontrast_df1 <- as.data.frame(summary(contrast_results))
dldvispiccontrast_df1$p_value_stars <- cut(dldvispiccontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDvispicemm2 <- emmeans(DLDvispicm4, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDvispicemm2, contrast_spec)

# Convert to a data frame and add significance stars
dldvispiccontrast_df2 <- as.data.frame(summary(contrast_results))
dldvispiccontrast_df2$p_value_stars <- cut(dldvispiccontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

DLDvispicemm3 <- emmeans(DLDvispicm4, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDvispicemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
dldvispiccontrast_df3 <- as.data.frame(summary(contrast_results))
dldvispiccontrast_df3$p_value_stars <- cut(dldvispiccontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


DLDvispicemm4 <- emmeans(DLDvispicm4, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(DLDvispicemm4, contrast_spec)

# Convert to a data frame and add significance stars
dldvispiccontrast_df4 <- as.data.frame(summary(contrast_results))
dldvispiccontrast_df4$p_value_stars <- cut(dldvispiccontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
dldvispiccombined_df <- bind_rows(dldvispiccontrast_df1, dldvispiccontrast_df2,dldvispiccontrast_df3,dldvispiccontrast_df4)
```

#### TL data
##### Masked Word Data
Results:
- sig interaction of priming x ISI x region but no sig diffs btw priming conditions (overall, by hemisphere, by region, or by hemisphere and region)
```{r}
tlmaskedword_data$Priming <- contr_code_anova(tlmaskedword_data$Priming)
tlmaskedword_data$ISI <- contr_code_anova(tlmaskedword_data$ISI)
tlmaskedword_data$Region <- contr_code_anova(tlmaskedword_data$Region)
tlmaskedword_data$Hemisphere <- contr_code_anova(tlmaskedword_data$Hemisphere)

TLmaskedwordm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere +(1+Priming*ISI|Participant.ID), data=tlmaskedword_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(TLmaskedwordm4)%>%
  mutate(signif = stars.pval(p.value))

anova(TLmaskedwordm4)

emm1 <- emmeans(TLmaskedwordm4, pairwise ~ Priming*ISI | Region,adjust = "none")
emm1


TLmaskedwordemm1 <- emmeans(TLmaskedwordm4, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedwordemm1, contrast_spec)

# Convert to a data frame and add significance stars
tlmaskedwordcontrast_df1 <- as.data.frame(summary(contrast_results))
tlmaskedwordcontrast_df1$p_value_stars <- cut(tlmaskedwordcontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLmaskedwordemm2 <- emmeans(TLmaskedwordm4, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedwordemm2, contrast_spec)

# Convert to a data frame and add significance stars
tlmaskedwordcontrast_df2 <- as.data.frame(summary(contrast_results))
tlmaskedwordcontrast_df2$p_value_stars <- cut(tlmaskedwordcontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

TLmaskedwordemm3 <- emmeans(TLmaskedwordm4, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedwordemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
tlmaskedwordcontrast_df3 <- as.data.frame(summary(contrast_results))
tlmaskedwordcontrast_df3$p_value_stars <- cut(tlmaskedwordcontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLmaskedwordemm4 <- emmeans(TLmaskedwordm4, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedwordemm4, contrast_spec)

# Convert to a data frame and add significance stars
tlmaskedwordcontrast_df4 <- as.data.frame(summary(contrast_results))
tlmaskedwordcontrast_df4$p_value_stars <- cut(tlmaskedwordcontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
tlmaskedwordcombined_df <- bind_rows(tlmaskedwordcontrast_df1, tlmaskedwordcontrast_df2,tlmaskedwordcontrast_df3,tlmaskedwordcontrast_df4)
```
##### Masked Picture Data
Results:
- sig interaction of priming x region driven by sig diffs btw priming conditions at frontal region (p = .004) and priming x ISI x region driven by sig diffs btw priming conditions at ISI 67 @ frontal (typical priming effect) even when corrected for multiple comparisons
- uncorrected p-values: sig diffs btw priming conditions at ISI 67 @ frontal (typical priming effect), ISI 317 @ central (typical priming effect), ISI 67 @ occipital (unprimed more attenuated than primed--opposite of typical priming effect), ISI 67 @ left occipital (unprimed more attenuated than primed--opposite of typical priming effect), ISI 67 @ midline frontal (typical priming effect), ISI 317 @ midline central (typical priming effect), and ISI 67 @ right frontal (typical priming effect) 
```{r}
tlmaskedpic_data$Priming <- contr_code_anova(tlmaskedpic_data$Priming)
tlmaskedpic_data$ISI <- contr_code_anova(tlmaskedpic_data$ISI)
tlmaskedpic_data$Region <- contr_code_anova(tlmaskedpic_data$Region)
tlmaskedpic_data$Hemisphere <- contr_code_anova(tlmaskedpic_data$Hemisphere)

TLmaskedpicm4.celf <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere  + celf5.c + (1+Priming*ISI|Participant.ID), data=tlmaskedpic_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(TLmaskedpicm4.celf)%>%
  mutate(signif = stars.pval(p.value))

anova(TLmaskedpicm4.celf)

emm1 <- emmeans(TLmaskedpicm4.celf, pairwise ~ Priming | Region,adjust = "none")
emm1
emm2 <- emmeans(TLmaskedpicm4.celf, pairwise ~ Priming*ISI | Region,adjust = "none")
emm2


TLmaskedpicemm1 <- emmeans(TLmaskedpicm4.celf, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedpicemm1, contrast_spec)

# Convert to a data frame and add significance stars
tlmaskedpiccontrast_df1 <- as.data.frame(summary(contrast_results))
tlmaskedpiccontrast_df1$p_value_stars <- cut(tlmaskedpiccontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLmaskedpicemm2 <- emmeans(TLmaskedpicm4.celf, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedpicemm2, contrast_spec)

# Convert to a data frame and add significance stars
tlmaskedpiccontrast_df2 <- as.data.frame(summary(contrast_results))
tlmaskedpiccontrast_df2$p_value_stars <- cut(tlmaskedpiccontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

TLmaskedpicemm3 <- emmeans(TLmaskedpicm4.celf, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedpicemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
tlmaskedpiccontrast_df3 <- as.data.frame(summary(contrast_results))
tlmaskedpiccontrast_df3$p_value_stars <- cut(tlmaskedpiccontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLmaskedpicemm4 <- emmeans(TLmaskedpicm4.celf, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLmaskedpicemm4, contrast_spec)

# Convert to a data frame and add significance stars
tlmaskedpiccontrast_df4 <- as.data.frame(summary(contrast_results))
tlmaskedpiccontrast_df4$p_value_stars <- cut(tlmaskedpiccontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
tlmaskedpiccombined_df <- bind_rows(tlmaskedpiccontrast_df1, tlmaskedpiccontrast_df2,tlmaskedpiccontrast_df3,tlmaskedpiccontrast_df4)
```
##### Visible Word Data
Results:
- sig interaction of priming x region driven by sig diffs btw priming conditions at central region (p = .003) when corrected for multiple comparisons (unccorrected p-values: also driven by sig diffs btw priming conditions at frontal (p = .026) and occipital region (p = .019))
- when corrected for multiple comparisons, sig diffs btw priming conditions at ISI 317 @ central (typical priming effect)
- uncorrected p-values: sig diffs btw priming conditions at ISI 317 @ frontal (typical priming effect), ISI 317 @ central (typical priming effect), ISI 67 @ occipital (unprimed more attenuated than primed--opposite of typical priming effect), ISI 317 @ right central (typical priming effect)
```{r}
tlvisword_data$Priming <- contr_code_anova(tlvisword_data$Priming)
tlvisword_data$ISI <- contr_code_anova(tlvisword_data$ISI)
tlvisword_data$Region <- contr_code_anova(tlvisword_data$Region)
tlvisword_data$Hemisphere <- contr_code_anova(tlvisword_data$Hemisphere)

TLviswordm4.langstat.wrmt <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + lang.stat.c  +  wrmt.c + (1+Priming*ISI|Participant.ID), data=tlvisword_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(TLviswordm4.langstat.wrmt)%>%
  mutate(signif = stars.pval(p.value))

anova(TLviswordm4.langstat.wrmt)

emm1 <- emmeans(TLviswordm4.langstat.wrmt, pairwise ~ Priming | Region,adjust = "none")
emm1


TLviswordemm1 <- emmeans(TLviswordm4.langstat.wrmt, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLviswordemm1, contrast_spec)

# Convert to a data frame and add significance stars
tlviswordcontrast_df1 <- as.data.frame(summary(contrast_results))
tlviswordcontrast_df1$p_value_stars <- cut(tlviswordcontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLviswordemm2 <- emmeans(TLviswordm4.langstat.wrmt, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLviswordemm2, contrast_spec)

# Convert to a data frame and add significance stars
tlviswordcontrast_df2 <- as.data.frame(summary(contrast_results))
tlviswordcontrast_df2$p_value_stars <- cut(tlviswordcontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

TLviswordemm3 <- emmeans(TLviswordm4.langstat.wrmt, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLviswordemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
tlviswordcontrast_df3 <- as.data.frame(summary(contrast_results))
tlviswordcontrast_df3$p_value_stars <- cut(tlviswordcontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLviswordemm4 <- emmeans(TLviswordm4.langstat.wrmt, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLviswordemm4, contrast_spec)

# Convert to a data frame and add significance stars
tlviswordcontrast_df4 <- as.data.frame(summary(contrast_results))
tlviswordcontrast_df4$p_value_stars <- cut(tlviswordcontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
tlviswordcombined_df <- bind_rows(tlviswordcontrast_df1, tlviswordcontrast_df2,tlviswordcontrast_df3,tlviswordcontrast_df4)
```
##### Visible Picture Data
Results:
- sig main effect of priming and sig interaction of priming x region driven by sig diffs btw priming conditions at front (p < .001), central (p < .001), and occipital regions (p = .006) even when corrected for multiple comparisons
- when corrected for multiple comparisons, sig diffs btw priming conditions at ISI 317 overall (typical priming effect), ISI 67 @ frontal (typical priming effect), ISI 317 @ frontal (typical priming effect), ISI 67 @ central (typical priming effect), ISI 317 @ central (typical priming effect), and ISI 317 @ right frontal (typical priming effect)
- uncorrected p-values: sig diffs btw priming conditions at all of the above and at ISI 317 @ midline (typical priming effect), ISI 317 @ right (typical priming effect), ISI 67 @ occipital (unprimed more attenuated than primed--opposite of typical priming effect), ISI 317 @ left frontal (typical priming effect), ISI 317 @ midline frontal (typical priming effect), ISI 67 @ midline central (typical priming effect), ISI 317 @ midline central (typical priming effect), ISI 67 @ right frontal (typical priming effect), ISI 67 @ right central (typical priming effect), and ISI 317 @ right central (typical priming effect)
```{r}
tlvispic_data$Priming <- contr_code_anova(tlvispic_data$Priming)
tlvispic_data$ISI <- contr_code_anova(tlvispic_data$ISI)
tlvispic_data$Region <- contr_code_anova(tlvispic_data$Region)
tlvispic_data$Hemisphere <- contr_code_anova(tlvispic_data$Hemisphere)

TLvispicm4 <- lmer(Mean.Amp ~ Priming*ISI*Region*Hemisphere + (1+Priming*ISI|Participant.ID), data=tlvispic_data,REML=TRUE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tidy(TLvispicm4)%>%
  mutate(signif = stars.pval(p.value))

anova(TLvispicm4)

emm1 <- emmeans(TLvispicm4, pairwise ~ Priming | Region,adjust = "none")
emm1

TLvispicemm1 <- emmeans(TLvispicm4, ~ Priming * ISI)
# Define the contrasts of interest
contrast_spec <- list(
  "unprimed 67 vs primed 67" = c(-1, 1, 0, 0),
  "unprimed 317 vs primed 317" = c(0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLvispicemm1, contrast_spec)

# Convert to a data frame and add significance stars
tlvispiccontrast_df1 <- as.data.frame(summary(contrast_results))
tlvispiccontrast_df1$p_value_stars <- cut(tlvispiccontrast_df1$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLvispicemm2 <- emmeans(TLvispicm4, ~ Priming*ISI*Hemisphere)
# Define the contrasts of interest for each level of hemisphere
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ left" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ midline" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ midline" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ right" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLvispicemm2, contrast_spec)

# Convert to a data frame and add significance stars
tlvispiccontrast_df2 <- as.data.frame(summary(contrast_results))
tlvispiccontrast_df2$p_value_stars <- cut(tlvispiccontrast_df2$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))

TLvispicemm3 <- emmeans(TLvispicm4, ~ Priming*ISI*Region)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  "unprimed 67 vs primed 67 @ frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0),
  "unprimed 317 vs primed 317 @ occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLvispicemm3, contrast_spec)
contrast_results

# Convert to a data frame and add significance stars
tlvispiccontrast_df3 <- as.data.frame(summary(contrast_results))
tlvispiccontrast_df3$p_value_stars <- cut(tlvispiccontrast_df3$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


TLvispicemm4 <- emmeans(TLvispicm4, ~ Priming*ISI*Region*Hemisphere)
# Define the contrasts of interest for each level of region
contrast_spec <- list(
  # frontal
  "unprimed 67 vs primed 67 @ left frontal" = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left frontal" = c(0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left central" = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left central" = c(0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 317 vs primed 317 @ left parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  "unprimed 67 vs primed 67 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
 "unprimed 317 vs primed 317 @ left occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),

    # midline
    "unprimed 67 vs primed 67 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ midline occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
 
    # right
    "unprimed 67 vs primed 67 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right frontal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right central" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 0, 0,  0),
  "unprimed 317 vs primed 317 @ right parietal" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0,  0),
  "unprimed 67 vs primed 67 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1, 0,  0),
  "unprimed 317 vs primed 317 @ right occipital" = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, 1))

# Get the contrast results
contrast_results <- contrast(TLvispicemm4, contrast_spec)

# Convert to a data frame and add significance stars
tlvispiccontrast_df4 <- as.data.frame(summary(contrast_results))
tlvispiccontrast_df4$p_value_stars <- cut(tlvispiccontrast_df4$p.value,
                                 breaks = c(-Inf, 0.001, 0.01, 0.05, Inf),
                                 labels = c("***", "**", "*", ""))


# Bind the data frames together
tlvispiccombined_df <- bind_rows(tlvispiccontrast_df1, tlvispiccontrast_df2,tlvispiccontrast_df3,tlvispiccontrast_df4)
```